# 全球多资产策略 Into on Global Multi-asset Strategy {-}

`In Progress`

```{r eval=FALSE, include=FALSE}
<span style="color:red;font-weight:700;font-size:28px">DEMO ONLY: Internal Version</span>  
<span style="color:red;font-weight:700;font-size:28px">内部版本 请勿外传</span> 
```

## 全球战略资产配置策略 Global Tactical Asset Allocation Strategy (GTAA) {-} 

`In Progress`

The Global Tactical Asset Allocation Strategy (GTAA) is a top-down global macro strategy that seeks to identify and exploit inefficiencies between markets, regions, countries, and sectors. The research and decision-making process is fundamentally driven and discretionary but supported by extensive quantitative research. The strategy invests across global asset classes, including stocks, bonds, currencies, and commodities. 

**全球战略资产配置策略（GTAA）**是一种自上而下的全球宏观策略，旨在识别并利用市场、地区、国家和行业之间的效率差异。研究和决策过程基于基本面，具有自主性，但得到了广泛的量化研究支持。该策略投资于全球各类资产，包括股票、债券、货币和商品。

```{r eval=FALSE, include=FALSE}
Morgan Stanley (https://www.morganstanley.com/im/en-us/individual-investor/strategies/solutions-and-multi-asset/global-tactical-asset-allocation.html)
```

## 投资策略 GTAA Investment Strategy {-}

GTAA is a top-down investment strategy.
It heavily adapts from the All-weather Strategy by Bridgewater Associates.
The strategy aims to utilize various asset classes globally (Equities, ETFs, Bonds, FXs, and Cash) to capture maximum risk-adjusted returns for the entire duration of our investment.
The flexibility in adjusting allocation among asset classes, regions, and sectors is a key advantage.
Based on the Market Timing Hypothesis, this strategy is a widely applied multi-asset portfolio management methodology in mimicking risks, enabling investors to determine optimal entry and exit points for high-yield/risky and less-risky asset classes.

GTAA 投资策略:

GTAA是一种自上而下的投资策略。
该策略在很大程度上借鉴了*Bridgewater Associates*的全天候策略。
策略旨在全球范围内利用各种资产类别（股票、ETF、债券、外汇和现金）来获取我们整个投资期间的最大风险调整收益。
在资产类别、地区和行业之间调整配置的灵活性是其一大优势。
基于市场时机假设，该策略是一种广泛应用的多资产组合管理方法，用于模拟风险，使投资者能够确定高收益/高风险资产类别和低风险资产类别的最佳进入和退出点。


## 投资范围与建立组合 Investment Scope & Portfolio Construction {-}

`In Progress`



Use EM and Tech stocks as major risky assets, hedged by 10Y US-Govt Bonds, Gold futures, and Cash/CDs.
Asset allocation and timing (TAA) heavily depend on global macros, fundamentals, and quantitative asset allocation and portfolio optimization models.
Investment timing: when to enter or exit positions.
Investment class choices include Equities vs. Fixed Income products, small cap vs. large cap, value vs. growth.
Global scope and timing (G): region, country, and sector selections within asset classes: DM vs. EM (FI products, Equities, ETFs, FX deviations) and which specific country/region.


以新兴市场和科技股作为主要风险资产，通过美国10年期政府债券、黄金期货和现金/定期存款进行对冲。
资产配置和择时（TAA）：配置比例依赖于全球宏观经济、基本面和资产配置及投资组合优化的多策略量化模型。
投资时机：何时进入或退出头寸。
投资类别选择：股票与固定收益产品、小盘股与大盘股、价值股与成长股。
全球范围和时机（G）：在资产类别内选择地区、国家和行业：发达市场与新兴市场（固定收益产品、股票、ETF、外汇波动）及具体的国家/地区。

Use emerging markets and technology stocks as the primary risky assets, hedged with 10-year U.S. government bonds, gold futures, and cash/certificates of deposit.
Asset Allocation and Timing (TAA): The allocation percentages are heavily dependent on global macroeconomic conditions, fundamentals, and quantitative asset allocation and portfolio optimization models.
Investment Timing: Determining when to enter or exit positions.
Investment Class Choices: Equities vs. fixed income products, small cap vs. large cap, value vs. growth stocks.
Global Scope and Timing (G): Choices of regions, countries, and sectors within asset classes: developed markets vs. emerging markets (Fixed Income products, Equities, ETFs, FX deviations), and specific country/region selections.  

投资组合构建:

使用新兴市场和科技股作为主要风险资产，通过美国10年期政府债券、黄金期货和现金/定期存款进行对冲。
资产配置和择时（TAA）：配置比例极大地依赖于全球宏观经济状况、基本面以及量化资产配置和投资组合优化模型。
投资时机：确定进入或退出头寸的时机。
投资类别选择：股票与固定收益产品、小盘股与大盘股、价值股与成长股。
全球范围和时机（G）：在资产类别内选择地区、国家和行业：发达市场与新兴市场（固定收益产品、股票、ETF、外汇波动），以及具体的国家/地区选择。


## 投研流程 Investment & Research Process {-} 

`In Progress`

Investment Research Process - GTAA-based Portfolio:

Our team maintains an active management approach in constructing portfolios that maximize long-term risk-adjusted returns, which are suitable for the investors' needs and risk tolerance.
We select from various asset classes and securities globally that are most appropriate given the current market dynamics, aiming for maximum long-term risk-adjusted returns while proactively controlling the maximum drawdown.
Risk Management: We have a moderate risk preference in asset allocations and actively manage risks specific to securities and sudden market shifts. Tools include stop-loss levels, stress tests, and an internal risk management team.  


投资研究流程 - 基于GTAA的投资组合：

我们的团队采取主动管理的模式，以构建可长期持有的投资组合为目的，最大化风险调整回报，同时符合投资者的投资需求和风险承受能力。
在全球范围内选择各种资产类别和证券，在考虑当前市场动态下，旨在实现最大的长期风险调整回报，同时积极控制最大回撤。
风险管理：在资产配置上偏好中度风险，并针对特定证券风险和突发市场变动进行积极的风险管理。工具包括：止损水平线、压力测试和内部风险管理团队。




## 风险管理 Risk Management {-} 

`In Progress`


<div style="text-align: right;">
**返回目录  **[快速索引 Quick Table of Contents] 
</div>




<!-- Disclaimer section with a gray bar -->
<div style="width: 100%; height: 20px; background-color: grey;"></div>

<!-- Disclaimer Text -->
<div style="padding: 20px; margin-top: 20px; background-color: #f1f1f1;">
    内部资料，请勿外传! 

    Internal documents, please do not disseminate! 

    本网页模型搭建说明及模型网络应用仅供参考。无论是所含信息还是所表达的观点，
    均不得明示或暗示为任何形式的建议、提供、招揽、邀请、广告、诱导、推荐或代表，
    以买卖任何证券、金融工具或任何投资或其他特定产品。

    The web-based Quantitative Model e-Manual and web application are for information
    purposes only. The information and opinion contained and expressed herein, shall not,
    and shall not be deemed to, construed, expressly or impliedly, as advice, offer or
    solicitation of an offer, invitation, advertisement, inducement, recommendation, or
    representation of any kind or form whatsoever to buy or sell any security, financial
    instrument or any investment or other specific product.
</div>







