# 快速索引 Quick Table of Contents {-}  

```{r eval=FALSE, include=FALSE}
<span style="color:red;font-weight:700;font-size:28px">DEMO ONLY: Internal Version</span>  
<span style="color:red;font-weight:700;font-size:28px">内部版本 请勿外传</span> 
``` 

## $\diamondsuit$ 多资产策略网页APP入口 MAS Webapp Entrance {-}

[MAS-Stock Selection Webapp](https://webapp.multi-asset-strategy.cn)

```{r toc-1, echo=FALSE}
knitr::include_url("https://maswebapp.com")
```


## $\diamondsuit$ 全球多资产策略 Into on Global Multi-asset Strategy {-} 

* [全球多资产策略 Into on Global Multi-asset Strategy] for the overview on the Global Tactical Asset Allocation Strategy   [`Multi-asset Strategy Overview`]   

## $\diamondsuit$ 选股模型 Stock Selection Model {-} 
* [投资策略及模型规划 Investment Strategy Outlook ] for **Investment Thesis** and **Model Planning & Considerations** [`选股模型 Stock Selection Model`]   

### [基础模型：技术指标选股工具 The Base Model: a Technical Signaling Tool for Stock Selection ]{style="color:blue"} {-}

* [基础模型搭建 (Base) Model Construction] for **Model Construction** steps and the **Subjective Filters** [`基础选股模型 Stock Selection Model (Base)`]  

* [技术指标搭建 Technical Indicators Construction] for the construction of all **Technical Indicators** used [`基础选股模型 Stock Selection Model (Base)`]  

* [选取有效的技术指标（动态更新）Dynamic: Selecting Effective Technical Indicators] for the **dynamically** selection process of the **significant** **technical indicators** [`基础选股模型 Stock Selection Model (Base)`]  

* [基础模型选股表现 (Base) Model Performance] for the `base` **model performance** and **backtest** results [`基础选股模型 Stock Selection Model (Base)`]  

### [完整模型：基于量化指标的全面选股工具 The Complete Model: a Comprehensive Stock Selection Model: Using Quantitative Indicators]{style="color:blue"} {-}

`TBD`

## $\diamondsuit$ 其他资产量化模型 Quantitative Model for other Assets {-}  

`TBD`

## $\diamondsuit$ 资产配置量化模型 Asset Allocation Strategy Using Quantitative Models {-}  
 
`TBD`

## $\diamondsuit$ 组合风险控制和优化 Portfolio Risk Management & Optimization {-} 

* [风险披露 Risk Disclosure ] for the model and portfolio **risks** [`Multi-asset Strategy Quant Approach`]  


## $\diamondsuit$ 附录 Appendix {-} 

* [附录 Appendix] for the codes and our resources [`Multi-asset Strategy Quant Approach`]  




<!-- Disclaimer section with a gray bar -->
<div style="width: 100%; height: 20px; background-color: grey;"></div>

<!-- Disclaimer Text -->
<div style="padding: 20px; margin-top: 20px; background-color: #f1f1f1;">
    内部资料，请勿外传! 

    Internal documents, please do not disseminate! 

    本网页模型搭建说明及模型网络应用仅供参考。无论是所含信息还是所表达的观点，
    均不得明示或暗示为任何形式的建议、提供、招揽、邀请、广告、诱导、推荐或代表，
    以买卖任何证券、金融工具或任何投资或其他特定产品。

    The web-based Quantitative Model e-Manual and web application are for information
    purposes only. The information and opinion contained and expressed herein, shall not,
    and shall not be deemed to, construed, expressly or impliedly, as advice, offer or
    solicitation of an offer, invitation, advertisement, inducement, recommendation, or
    representation of any kind or form whatsoever to buy or sell any security, financial
    instrument or any investment or other specific product.
</div>








