## <span style="color:blue">技术指标3：指数平滑移动平均线 Technical Indicator 3: Moving Average Convergence Divergence (MACD)</span>   

<span style="color:red;font-weight:700;font-size:18px">Internal Version, DO NOT disseminate!</span>  
  
<span style="color:red;font-weight:700;font-size:18px">内部版本 请勿外传!</span> 


```{r 303-98, message=FALSE, warning=FALSE, include=FALSE}
# Define function to read another rmd file
source_rmd <- function(file, local = FALSE, ...){
  options(knitr.duplicate.label = 'allow')

  tempR <- tempfile(tmpdir = ".", fileext = ".R")
  on.exit(unlink(tempR))
  knitr::purl(file, output=tempR, quiet = TRUE)

  envir <- globalenv()
  source(tempR, local = envir, ...)
}
```

```{r 303-99, message=FALSE, warning=FALSE, include=FALSE}
# Read in base model construction rmd to continue with 3.2
source_rmd("03_b_EMA.Rmd")
```



`In Progress`

Includes `tsignal7`, `tsignal8`, and `tsignal9`

包括交易信号 `tsignal7`, `tsignal8`, 以及 `tsignal9` 


### **MACD**简介 Intro- **MACD**: 

`In Progress`

指数平滑移动平均线

异同移动平均线

Mathematically defined as: 数学上定义为：

$$\text{MACD}_{t}(S, L) = \text{EMA}_{t}(P, S) - \text{EMA}_{t}(P, L)$$  

Alternatively, written as:  

$$\text{MACD}_{t}(\text{close, fast, slow}) = \text{EMA}_{t}(\text{close, fast}) - \text{EMA}_{t}(\text{close, slow})$$  

$$\text{Signal}_{t}(S, L, K) = \text{EMA}_{t}(\text{MACD}(S, L), K)$$   

Histogram of **MACD**:  

$$\text{Histogram}_{t}=\text{MACD}_{t}-\text{Signal}_{t}$$

Percentage format of **MACD**:  

$$\text{MACD}_{t}(S, L) = \frac{\text{EMA}_{t}(P, S) - \text{EMA}_{t}(P, L)}{\text{EMA}_{t}(P, L)}$$



`In Progress`



```{r 303-1, echo=FALSE, message=FALSE, warning=FALSE}
# Define a function to compute the value for EMA using the adjusted close price with parameter settings of n days (for other indicators other than EMA)

EMA_comput_for_others <- function(price, n) {
  ema <- rep(0, length(price))
  ema[1] <- price[1]
  beta <- 2 / (n + 1)
  # Calculate EMA
  for (i in 2:length(price)) {
    ema[i] <- (price[i] * beta) + (ema[i - 1] * (1 - beta))
  }
  return(ema)
}
```

```{r 303-2, echo=FALSE, message=FALSE, warning=FALSE}
# Define three functions to compute the values for MACD using the adjusted close price with parameter settings of S, L, K
# S=nFast is the short period, L=nSlow is the long period, K=nSig is the signal smoothing period
# MACD line, MACD signal, MACD histogram

MACD_line_comput <- function(price, S, L) {
  EMA_short <- EMA_comput_for_others(price, S)
  EMA_long <- EMA_comput_for_others(price, L)
  MACD <- EMA_short - EMA_long
  return(MACD)
}

MACD_signal_comput <- function(MACD, K) {
  signal <- EMA_comput_for_others(MACD, K)
  return(signal)
}

MACD_histogram_comput <- function(MACD, signal) {
  histogram <- MACD - signal
  return(histogram)
}

```

```{r 303-3, echo=FALSE, message=FALSE, warning=FALSE}
# Compute MACD for all stocks, Full Data
# Include MACD line, MACD signal, MACD histogram
mega7data_modified <-
  mega7data_modified %>%
  group_by(symbol) %>%
  mutate(MACD_line = MACD_line_comput(adjusted, S = 12, L = 26),
         MACD_signal = MACD_signal_comput(MACD_line,  K = 9),
         MACD_histogram = MACD_histogram_comput(MACD_line, MACD_signal))
```

```{r 303-4, echo=FALSE, message=FALSE, warning=FALSE}
# Alternative way: 
# Below utilizes the `TTR` package directly for MACD computations: MACD()
#AAPL <- xts(macd_value_result_pdf$adjusted,macd_value_result_pdf$date)
#macd <- MACD(AAPL, nFast = 12, nSlow = 26, nSig = 9, 
#  percent = FALSE, maType = EMA)
```

```{r 303-5, message=FALSE, warning=FALSE, include=FALSE}
macd_value_result <- 
  mega7data_modified %>%
  mutate(date = as.Date(date)) %>%
  select(date, adjusted, MACD_line, MACD_signal,
         MACD_histogram, volume) %>%
  arrange(desc(date)) %>%
  head(5000)

macd_value_result_pdf <- 
  mega7data_modified %>%
  slice(which(symbol == "AAPL")) %>%
  mutate(date = as.Date(date)) %>%
  select(date, adjusted, MACD_line, MACD_signal,
         MACD_histogram, volume) %>%
  arrange(desc(date))
```

```{r 303-6, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
# NOT FINISHED

# ##### [Code Hidden 代码已隐藏]{style="color:red"} {-}

# ##### [Individual stock outputs are suppressed, only `AAPL.US` related results are shown for illustration purposes. Refer to the *webapp* or the `html` version of the *e-Manual* for complete outputs. 个股输出数据及图表已隐藏，报告仅展示`苹果公司(AAPL.US)`的相关结果,完整图表可参阅*webapp* 或网页版*Global MAS 量化模型搭建说明*。]{style="color:red"} {-}

# pdf output
# Display AAPL output (EMA values)
kbl(head(ema_value_result_pdf,10), booktabs = T, linesep = '', digits = 1,
    caption = "EMA Computations for AAPL.US",
    format.args = list(big.mark = ",", scientific = FALSE),
    col.names = c("Symbol","Date","Adj Close","EMA5","EMA8",
                  "EMA13","EMA20","EMA50","EMA200","Volume")) %>%
  kable_styling(latex_options = c("striped", "scale_down",
                                  "HOLD_position"), 
                position = "center") %>%
  column_spec(c(1,4:9), bold = T) %>%
  kableExtra::footnote(general = "Output 3.2.a: Latest 10 rows of data are shown.")
```

##### [Code Hidden 代码已隐藏]{style="color:red"} {-}

##### [Enter the ticker/symbol in the search box for stock-specific results. Sort tool is available next to the variable names. 搜索框中输入股票代码可以过滤展示个股相关结果。点击变量名旁的箭头可进行排序。]{style="color:purple"} {-}

```{r 303-7, echo=FALSE, message=FALSE, warning=FALSE}
# html output
# Display MACD values
DT::datatable(macd_value_result, 
              colnames = c('Symbol' = 2, 'Date' = 3, 'Adjusted' = 4, 'MACD Line' = 5,
                           'MACD Signal' = 6, 'MACD Histogram' = 7, 'Volume' = 8),
              caption = htmltools::tags$caption(style = 'caption-side: top; 
                                            text-align: center; color: black; 
                                            font-size: 200%;',
                                            'MACD Computations'),
              options = list(pageLength = 10, lengthMenu = c(5, 10, 15, 20),
              searching = TRUE, style = list(width = '100%')), extensions = 'Buttons') %>%
  formatRound(columns = c('Adjusted','MACD Line', 'MACD Signal', 'MACD Histogram'),
              digits = 2)  %>%
  formatRound(columns = 'Volume', digits = 0)
```

Output 3.3.a: **MACD** Computations, latest 10 rows of data are shown.  

图表 3.3.a: **MACD** 计算结果，展示最新的 10 行数据。

</br>




`In Progress`



```{r 303-8, message=FALSE, warning=FALSE, include=FALSE}
# Data manipulation for MACD plot TLSA.US
macd_aapl_xts <- 
  mega7data_modified %>%
  slice(which(symbol == "AAPL")) %>%
  mutate(date = as.POSIXct(date)) %>%
  select(date, open, high, low, close, volume, adjusted) %>%
  na.omit()

open <- macd_aapl_xts$open
high <- macd_aapl_xts$high
low <- macd_aapl_xts$low
close <- macd_aapl_xts$close
adjusted <- macd_aapl_xts$adjusted
volume <- as.numeric(macd_aapl_xts$volume)

macd_aapl_xts <- xts(cbind(open, high, low, close, volume, adjusted),
                   as.POSIXct(macd_aapl_xts$date))
macd_aapl_xts <- last(macd_aapl_xts,'365 days')
```

```{r 303-9, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
##### AAPL MACD Plot using `TTR` package {-}
# pdf plot
# MACD plot TLSA.US under settings fast = 12, slow = 26, signal = 9, type = "EMA"
chartSeries(macd_aapl_xts,
            theme = chartTheme('black'))
addMACD(fast = 12,slow = 26,signal = 9,type = "EMA")
```


### 交易信号与策略- **MACD** Trading signal(s) & strategies- **MACD**:


`In Progress`


```{r eval=FALSE, include=FALSE}
MACD 的使用方法：
1）交叉信号：当 MACD 线从下方穿过信号线（形成“金叉”），可能是买入的信号。反之，如果 MACD 线从上方穿过信号线（形成“死叉”），可能是卖出的信号。
2）背离信号：如果价格创新高，但 MACD 没有创新高（形成“顶部背离”），可能预示着市场可能会转向下跌。反之，如果价格创新低，但 MACD 没有创新低（形成“底部背离”），可能预示着市场可能会转向上涨。
3）柱状图：当柱状图从负值转为正值，可能是一个买入信号。反之，如果柱状图从正值转为负值，可能是一个卖出信号。
```


### **MACD**策略交易信号汇总 To summarize for **MACD** trading signals: 

-   **MACD**- `tsignal7`:\
    **BUY**: $\text{MACD Line}$ cross from **below to above** $\text{MACD Signal}$,\
    **SELL**: $\text{MACD Line}$ cross from **above to below** $\text{MACD Signal}$, \
    **HOLD**: otherwise;  
    
- **MACD**交易信号- `tsignal7`:\
    **买入**: $\text{MACD线}$ **从下方穿越至** $\text{MACD信号线}$**上方**,\
    **卖出**: $\text{MACD线}$ **从上方穿越至** $\text{MACD信号线}$**下方**,\
    **持有**: 其他情况;

-   **MACD**- `tsignal8`:\
    **BUY**: $\text{MACD Histogram}$ cross from **below zero to above zero**,\
    **SELL**: $\text{MACD Histogram}$ cross from **above zero to below zero**, \
    **HOLD**: otherwise;  
    
- **MACD**交易信号- `tsignal8`:\
    **买入**: $\text{MACD柱状图}$ **从负值升至正值**,\
    **卖出**: $\text{MACD柱状图}$ **从正值降至负值**,\
    **持有**: 其他情况;

`In Progress`

-   **MACD**- `tsignal9`:\
    **BUY**: ,\
    **SELL**: , \
    **HOLD**: otherwise.   
    
- **MACD**交易信号- `tsignal9`:\
    **买入**: **MACD底部背离**,\
    **卖出**: **MACD顶部背离**,\
    **持有**: 其他情况。

```{r 303-10, message=FALSE, warning=FALSE, include=FALSE}
# MACD Trading Signal 7: MACD Line > MACD Signal
# MACD Trading Rule setup and Generate Signals 
mega7data_modified <- 
  mega7data_modified %>%
  group_by(symbol) %>%
  mutate(tsignal7 = case_when(
    lag(MACD_line) < lag(MACD_signal) & MACD_line > MACD_signal ~ 'BUY',
    lag(MACD_line) >= lag(MACD_signal) & MACD_line < MACD_signal ~ 'SELL',
    lag(MACD_line) < lag(MACD_signal) & MACD_line <= MACD_signal ~ 'HOLD',
    lag(MACD_line) >= lag(MACD_signal) & MACD_line >= MACD_signal ~ 'HOLD'))
```

```{r 303-11, message=FALSE, warning=FALSE, include=FALSE}
# MACD Trading Signal 8: MACD Histogram > 0
# MACD Trading Rule setup and Generate Signals 
mega7data_modified <- 
  mega7data_modified %>%
  group_by(symbol) %>%
  mutate(tsignal8 = case_when(
    lag(MACD_histogram) < 0 & MACD_histogram > 0 ~ 'BUY',
    lag(MACD_histogram) >= 0 & MACD_histogram < 0 ~ 'SELL',
    lag(MACD_histogram) < 0 & MACD_histogram <= 0 ~ 'HOLD',
    lag(MACD_histogram) >= 0 & MACD_histogram >= 0 ~ 'HOLD'))
```

```{r 303-12, message=FALSE, warning=FALSE, include=FALSE}
# NOT FINISHED

# MACD Trading Signal 9: 
# MACD Trading Rule setup and Generate Signals 

```


```{r 303-13, message=FALSE, warning=FALSE, include=FALSE, paged.print=TRUE}
# Prepare data frame MACD signal results

# NOT FINISHED 
# ADD SIGNAL 9

macd_signal_result <-
  mega7data_modified %>%
  select(date, symbol, adjusted, tsignal7, tsignal8) %>%
  arrange(desc(date)) %>%
  head(5000)

# For AAPL signals results (MACD)
macd_signal_result_pdf <-
  mega7data_modified %>%
  slice(which(symbol == "AAPL")) %>%
  ungroup() %>%
  select(date, symbol, adjusted, tsignal7, tsignal8) %>%
  arrange(desc(date)) %>%
  head(10)
```

```{r 303-14, eval=FALSE, fig.pos='H', message=FALSE, warning=FALSE, include=FALSE}
# ##### [Code Hidden 代码已隐藏]{style="color:red"} {-}

# ##### [Individual stock outputs are suppressed, only `AAPL.US` related results are shown for illustration purposes. Refer to the *webapp* or the `html` version of the *e-Manual* for complete outputs. 个股输出数据及图表已隐藏，报告仅展示`苹果公司(AAPL.US)`的相关结果,完整图表可参阅*webapp* 或网页版*Global MAS 量化模型搭建说明*。]{style="color:red"} {-}

# NOT FINISHED 
# ADD SIGNAL 9

# pdf output
# Display AAPL signal results (EMA signals)
kbl(ema_signal_result_pdf, booktabs = T, linesep = "", longtable = T, 
    digits = 1, caption = "EMA Trading Signals for AAPL.US", 
    format.args = list(big.mark = ",", scientific = FALSE),
    col.names = c("Date","Symbol","Adj Close","tsignal4","tsignal5",
                  "tsignal6","tsignal6a","tsignal6b")) %>%
  kable_styling(latex_options = c("striped", "scale_up",
                                  "HOLD_position"),
                full_width = F) %>%
  column_spec(c(2,4:6), bold = T) %>%
  column_spec(1, width = "1.9cm") %>%
  kableExtra::footnote(general = "Output 3.2.b: latest 10 rows of data are shown.",
              number = "Includes tsignal4, tsignal5, tsignal6, tsignal6a and tsignal6b.")
#图表3.2.b: EMA交易信号，展示最新的10行数据。包括`tsignal4`, `tsignal5`, `tsignal6`, #`tsignal6a`和`tsignal6b`。
```

##### [Code Hidden 代码已隐藏]{style="color:red"} {-}

##### [Enter the ticker/symbol in the search box for stock-specific results. Sort tool is available next to the variable names. 搜索框中输入股票代码可以过滤展示个股相关结果。点击变量名旁的箭头可进行排序。]{style="color:purple"} {-}

```{r 303-15, echo=FALSE, message=FALSE, warning=FALSE}
# html output
# Display MACD signal results 

# NOT FINISHED 
# ADD SIGNAL 9

DT::datatable(macd_signal_result, 
              colnames = c('Date' = 2, 'Symbol' = 3, 'Adjusted' = 4),
              caption = htmltools::tags$caption(style = 'caption-side: top; 
                                            text-align: center; color: black; 
                                            font-size: 200%;',
                                            'MACD Trading Signals'),
              options = list(pageLength = 10, lengthMenu = c(5, 10, 15, 20),
              searching = TRUE, style = list(width = '100%')), extensions = 'Buttons') %>%
    formatRound(columns = 'Adjusted', digits = 2)  
```

Output 3.3.b: **MACD** trading signals, latest 10 rows of data are shown. Includes `tsignal7`, `tsignal8`, and `tsignal9(IN PROCESS)`.  

图表3.3.b: **MACD**交易信号，展示最新的10行数据。包括`tsignal7`, `tsignal8`, 和`tsignal9(IN PROCESS)`。

```{r 303-16, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
# NOT FINISHED 
# ADD SIGNAL 9


# pdf output
# EMA Candlestick+Volume Plot for AAPL with trading signals
# Prepare the dataset for candlestick components
ema_signal_plot_pdf<- 
  mega7data_modified %>%
  slice(which(symbol == "AAPL")) %>%
  select(date, symbol, adjusted, open, close, high, low, volume, EMA5, 
         EMA8, EMA13, EMA20, EMA50, EMA200, tsignal4, tsignal5, tsignal6) %>%
  mutate(date = as.Date(date, format = "%Y-%m-%d"),
         day_trend_color = ifelse(open - adjusted > 0, "red", "green")) %>%
  filter(as.Date(date) > as.Date(Sys.Date()-months(12)))
```


```{r 303-17, eval=FALSE, fig.height=7, fig.width=10, message=FALSE, warning=FALSE, include=FALSE}
# NOT FINISHED 
# ADD SIGNAL 9

# pdf output
# EMA Candlestick+Volume Plot for AAPL with trading signals

# Candlestick Plot with EMA Trading Signals
color_values <- c(
  "EMA5" = "black", 
  "EMA8" = "yellow", 
  "EMA13" = "purple", 
  "EMA20" = "red", 
  "EMA50" = "grey", 
  "EMA200" = "blue",
  "green" = "darkgreen", 
  "red" = "red",
  "Signal4 BUY " = "lightgreen", 
  "Signal4 SELL" = "deeppink",
  "Signal5 BUY" = "lightgreen", 
  "Signal5 SELL" = "deeppink",
  "Signal6 BUY" = "lightgreen", 
  "Signal6 SELL" = "deeppink"
)

candlestick <- 
  ggplot(ema_signal_plot_pdf, aes(x = date)) +
  geom_segment(aes(xend = date, y = open, 
                   yend = adjusted, colour = day_trend_color), size = 5) +
  geom_segment(aes(xend = date, y = high, 
                   yend = low, colour = day_trend_color)) +
  geom_line(aes(y = EMA5, color = "EMA5"), size = 0.5) +
  geom_line(aes(y = EMA8, color = "EMA8"), size = 0.5) +
  geom_line(aes(y = EMA13, color = "EMA13"), size = 0.5) +
  geom_line(aes(y = EMA20, color = "EMA20"), size = 0.5) +
  geom_line(aes(y = EMA50, color = "EMA50"), size = 0.5) +
  geom_line(aes(y = EMA200, color = "EMA200"), size = 0.5) +

  # Adding trading signals with different shapes and colors
  geom_point(data = filter(ema_signal_plot_pdf, tsignal4 == "BUY"),
             aes(x = date, y = high, color = "Signal4 BUY", 
                 shape = "Signal4 BUY"), size = 2) +
  geom_point(data = filter(ema_signal_plot_pdf, tsignal4 == "SELL"), 
             aes(x = date, y = low, color = "Signal4 SELL", 
                 shape = "Signal4 SELL"), size = 2) +
  geom_point(data = filter(ema_signal_plot_pdf, tsignal5 == "BUY"), 
             aes(x = date, y = high, color = "Signal5 BUY", 
                 shape = "Signal5 BUY"), size = 2) +
  geom_point(data = filter(ema_signal_plot_pdf, tsignal5 == "SELL"), 
             aes(x = date, y = low, color = "Signal5 SELL", 
                 shape = "Signal5 SELL"), size = 2) +
  geom_point(data = filter(ema_signal_plot_pdf, tsignal6 == "BUY"), 
             aes(x = date, y = high, color = "Signal6 BUY", 
                 shape = "Signal6 BUY"), size = 2) +
  geom_point(data = filter(ema_signal_plot_pdf, tsignal6 == "SELL"), 
             aes(x = date, y = low, color = "Signal6 SELL", 
                 shape = "Signal6 SELL"), size = 2) +
  theme(legend.position = "top",
            guides(color = guide_legend(nrow = 4, byrow = TRUE, 
                                title = "Indicators & Signals"), 
    shape = guide_legend(nrow = 4, byrow = TRUE, title = "Trade Signals") 
  )) +
  scale_color_manual(name = "Indicators & Signals", values = color_values) +
  scale_shape_manual(name = "Signal Shapes", 
                     values = c("Signal4 BUY" = 17, "Signal4 SELL" = 4, 
                                "Signal5 BUY" = 18, "Signal5 SELL" = 3, 
                                "Signal6 BUY" = 15, "Signal6 SELL" = 1)) +
  labs(
    y = "Stock Price, in USD", x = "Date") +
    labs(title = paste0("Price Volume Candlestick Plot for TLSA.US \
       with EMA Lines and Trading Signals")) +
  theme_bw() +
  scale_x_date(date_breaks = "2 months", date_labels = "%b %Y")

# Volume Plot
volume_plot <- 
  ggplot(ema_signal_plot_pdf, aes(x = date, y = volume, fill = day_trend_color)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = c("green" = "darkgreen", "red" = "red")) +
  labs(y = "Daily Trading Volume", x = "Date") +
  theme_bw() +
  theme(legend.position = "none",
            guides(color = guide_legend(nrow = 4, byrow = TRUE, 
                                title = "Indicators & Signals"), 
    shape = guide_legend(nrow = 4, byrow = TRUE, title = "Trade Signals") 
  )) +
  scale_x_date(date_breaks = "2 months", date_labels = "%b %Y") +
  scale_y_continuous(labels = scales::comma)


# Combine 2 plots
ggarrange(candlestick, volume_plot, ncol = 1, nrow = 2,
    heights =c(9,3), widths = 10, align = "v") 

# Output 3.1.c: EMA plot with trading signals on Price and Volume, duration setting TTM.
```


```{r 303-18, echo=FALSE, message=FALSE, warning=FALSE}
# NOT FINISHED 
# ADD SIGNAL 9

# html output
# plotly interactive plot
# EMA Candlestick+Volume Plot for AAPL with trading signals
# Prepare the dataset 

macd_signal_plot_html<- 
  mega7data_modified %>%
  slice(which(symbol == "AAPL")) %>%
  select(date, symbol, adjusted, open, close, high, low, volume, MACD_line, 
         MACD_signal, MACD_histogram, tsignal7, tsignal8) %>%
  arrange(date) %>%
   mutate(
    prev_adjusted = lag(adjusted),
    prev_MACD_line = lag(MACD_line),
    prev_MACD_signal = lag(MACD_signal),
    prev_MACD_histogram = lag(MACD_histogram)) %>%
 mutate(date = as.Date(date, format = "%Y-%m-%d"),
         day_trend_color =  ifelse(open < adjusted, "lightgreen", "red"),
         prev_volume = lag(volume),
         prev_adjusted = lag(adjusted),
         volume_color = ifelse(volume > prev_volume, "orange", "lightblue"),
         hover_text_volume = paste(
      "<b>Symbol:</b>", symbol, "<br>",
      "<b>Date:</b>", format(date, '%Y-%m-%d'), "<br>",
      "<b>Daily Volume:</b>", formatC(volume, big.mark = ","),
      "<span style='color:", 
      ifelse(volume > prev_volume, "darkgreen", "red"), ";'>",
      ifelse(volume > prev_volume, "▲", "▼"), "</span>", "<br>")) %>% 
  filter(as.Date(date) > as.Date(Sys.Date()-months(12)))

# Define shapes for each signal
signal_shapes <- list(
  "Signal7 BUY" = "circle",
  "Signal7 SELL" = "circle-open",
  "Signal8 BUY" = "triangle-up",
  "Signal8 SELL" = "triangle-down-open"
)

macd_signal_plot_html <- 
  macd_signal_plot_html %>%
 mutate(hover_text = paste(
    "<b>Symbol:</b>", symbol, "<br>",
    "<b>Date:</b>", format(date, '%Y-%m-%d'), "<br>",
    "<b>Adjusted Close Price:</b> $", round(adjusted, 2), "<br>",
    "<span style='color:", 
    ifelse(adjusted > prev_adjusted, "darkgreen", "pink"), ";'>",
      ifelse(adjusted > prev_adjusted, "▲", "▼"), "</span>", "<br>",
    "<b>Open:</b> $", round(open, 2), "<br>",
    "<b>High:</b> $", round(high, 2), "<br>",
    "<b>Low:</b> $", round(low, 2), "<br>",
    "<b>Volume:</b>", formatC(volume, format = "f", big.mark = ","),
     "<span style='color:", 
      ifelse(volume > prev_volume, "darkgreen", "red"), ";'>",
      ifelse(volume > prev_volume, "▲", "▼"), "</span>", "<br>"
  ))


# Hover for MACD subplot
macd_signal_plot_html <- 
  macd_signal_plot_html %>%
  mutate(hover_text_macd = paste(
      "<b>Symbol:</b>", symbol, "<br>", 
      "<b>Date:</b>", format(date, '%Y-%m-%d'), "<br>",
      "<b>Adjusted Close Price:</b> $", round(adjusted, 2), 
      "<span style='color:", 
      ifelse(adjusted > prev_adjusted, "darkgreen", "red"), ";'>",
      ifelse(adjusted > prev_adjusted, "▲", "▼"), "</span>", "<br>",
      "<b>MACD Line:</b>", round(MACD_line, 2),
      "<span style='color:", 
      ifelse(MACD_line > prev_MACD_line, "darkgreen", "deeppink"), ";'>",
      ifelse(MACD_line > prev_MACD_line, "▲", "▼"), "</span>", "<br>",
      "<b>MACD Signal:</b>", round(MACD_signal, 2),
      "<span style='color:", 
      ifelse(MACD_signal > prev_MACD_signal, "darkgreen", "deeppink"), ";'>",
      ifelse(MACD_signal > prev_MACD_signal, "▲", "▼"), "</span>", "<br>",
      "<b>MACD Histogram:</b>", round(MACD_histogram, 2),
      "<span style='color:", 
      ifelse(MACD_histogram > prev_MACD_histogram, "darkgreen", "deeppink"), ";'>",
      ifelse(MACD_histogram > prev_MACD_histogram, "▲", "▼"), "</span>", "<br>"
    )
  )
```

##### [Code Hidden 代码已隐藏]{style="color:red"} {-}

##### [Individual stock outputs are suppressed, only `AAPL.US` related results are shown for illustration purposes. Refer to the *webapp* for the complete plot output. 个股输出数据及图表已隐藏，报告仅展示`苹果公司(AAPL.US)`的相关结果,完整图表可参阅*webapp*。]{style="color:red"} {-}

```{r 303-19, echo=FALSE,  message=FALSE, warning=FALSE}
# NOT FINISHED 
# ADD SIGNAL 9

# html output
# plotly interactive plot
# MACD Price Candlestick Plot for AAPL with trading signals

# Candlestick Plot with MACD Trading Signals
fig <- plot_ly(data = macd_signal_plot_html, type = "candlestick", 
               x = ~date, open = ~open, close = ~adjusted, high = ~high, low = ~low,
               increasing = list(line = list(color = "darkgreen", width = 10), 
                                 fillcolor = "darkgreen"),
               decreasing = list(line = list(color = "red", width = 10), 
                                 fillcolor = "red"), 
               hoverinfo = "text", text = ~hover_text, showlegend = FALSE) %>%
  add_markers(data = filter(macd_signal_plot_html, tsignal7 == "BUY"), 
              x = ~date, y = ~high, 
              marker = list(color = "lightgreen", size = 6,
                            symbol = signal_shapes[["Signal7 BUY"]]), 
              name = "Signal7 BUY", showlegend = TRUE,
              hoverinfo = "text",
              hovertemplate = 
                "<b>Date:</b> %{x|%Y-%m-%d}<br><b>Signal7 BUY</b><extra></extra>") %>%
  add_markers(data = filter(macd_signal_plot_html, tsignal7 == "SELL"), 
              x = ~date, y = ~low, 
              marker = list(color = "pink", size = 6,
                            symbol = signal_shapes[["Signal7 SELL"]]), 
              name = "Signal7 SELL", showlegend = TRUE,
              hoverinfo = "text",
              hovertemplate = 
                "<b>Date:</b> %{x|%Y-%m-%d}<br><b>Signal7 SELL</b><extra></extra>") %>%
  add_markers(data = filter(macd_signal_plot_html, tsignal8 == "BUY"), 
              x = ~date, y = ~high, 
              marker = list(color = "lightgreen", size = 6,
                            symbol = signal_shapes[["Signal8 BUY"]]), 
              name = "Signal8 BUY",  showlegend = TRUE,
              hoverinfo = "text",
              hovertemplate = 
                "<b>Date:</b> %{x|%Y-%m-%d}<br><b>Signal8 BUY</b><extra></extra>") %>%
  add_markers(data = filter(macd_signal_plot_html, tsignal8 == "SELL"), 
              x = ~date, y = ~low, 
              marker = list(color = "pink", size = 6,
                            symbol = signal_shapes[["Signal8 SELL"]]), 
              name = "Signal8 SELL", showlegend = TRUE,
              hoverinfo = "text",
              hovertemplate = 
                "<b>Date:</b> %{x|%Y-%m-%d}<br><b>Signal8 SELL</b><extra></extra>") 

# MACD subplot.
fig <- fig %>%
  add_trace(
    data = macd_signal_plot_html,
    x = ~date,
    y = ~MACD_histogram,
    type = 'bar',
    marker = list(color = ~ifelse(MACD_histogram >= 0, 'green', 'red')),
    name = 'Histogram',
    yaxis = 'y2',
    showlegend = TRUE,
    hover_info = 'text',
    text = ~hover_text_macd)

# Add the MACD and signal lines on the same subplot as the histogram
fig <- fig %>%
  add_trace(
    data = macd_signal_plot_html,
    x = ~date,
    y = ~MACD_line,
    type = 'scatter',
    mode = 'lines',
    line = list(color = 'darkgrey'),
    name = 'MACD Line',
    yaxis = 'y2', 
    showlegend = TRUE,
    hover_info = 'text',
    text = ~hover_text_macd) %>%
  add_trace(
    data = macd_signal_plot_html,
    x = ~date,
    y = ~MACD_signal,
    type = 'scatter',
    mode = 'lines',
    line = list(color = 'red'),
    name = 'MACD Signal',
    yaxis = 'y2',
    showlegend = TRUE,
    hover_info = 'text',
    text = ~hover_text_macd)

# Update the layout for the secondary y-axis without using 'overlaying' and set the domain for both y-axes
fig <- fig %>%
  layout(
    title = list(text = "Interactive Price Candlestick Plot for AAPL.US \
                      with MACD Subplot and Trading Signals",
                      x = 0.5,  
                      y = 1.2,  
                      xanchor = 'center',
                      yanchor = 'top'),
    yaxis = list(domain = c(0.4, 1), title = "Stock Price, in USD", 
                 fixedrange = FALSE),
    yaxis2 = list(domain = c(0, 0.25), title = "MACD", anchor = 'x', 
                  side = 'left', overlaying = NULL, fixedrange = FALSE),
    xaxis = list(domain = c(0, 1), title = "Date", anchor = 'y',
                      type = "date", 
                      rangeslider = list(visible = TRUE),
                      rangeselector = list(
                        buttons = list(
                          list(count = 1, label = "1w", 
                               step = "week", stepmode = "backward"),
                          list(count = 2, label = "2w", 
                               step = "week", stepmode = "backward"),
                          list(count = 1, label = "1m", 
                               step = "month", stepmode = "backward"),
                          list(count = 6, label = "6m", 
                               step = "month", stepmode = "backward"),
                          list(count = 12, label = "TTM", 
                               step = "month", stepmode = "backward"),
                          list(count = 1, label = "YTD",
                               step = "year", stepmode = "todate"),
                          list(count = 1, label = "1y", 
                               step = "year", stepmode = "backward"),
                          list(step = "all")
                      )
                    )),
    barmode = 'relative', # Use 'relative' to overlay MACD lines on the histogram
    legend = list(orientation = "h",x = 0, y = -0.5, 
                       xanchor = "left", yanchor = "top", traceorder = "normal"),
    margin = list(t = 100, b = 200),
    width = 900, height = 750
  )



# Display the plot
fig
```


Output 3.3.c: Interactive **MACD** plot with trading signals on Price, duration setting TTM.  

图表 3.3.c: 交互式**MACD**股价图表，包括**MACD**策略交易信号，时间设置为TTM。


##### [Code Hidden 代码已隐藏]{style="color:red"} {-}

##### [Individual stock outputs are suppressed, only `AAPL.US` related results are shown for illustration purposes. Refer to the *webapp* for the complete plot output. 个股输出数据及图表已隐藏，报告仅展示`苹果公司(AAPL.US)`的相关结果,完整图表可参阅*webapp*。]{style="color:red"} {-}

```{r 303-20, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}

# NOT FINISHED 
# ADD SIGNAL 9


# html output
# plotly interactive plot
# EMA Volume Plot for AAPL with trading signals
# Define signal colors and shapes for trading signals

volume_plot <- plot_ly(data = ema_signal_plot_html, 
                       x = ~date, y = ~volume, type = 'bar', 
                       marker = list(color = ~volume_color),
                       hoverinfo = 'text', text = ~hover_text_volume,
                       name = "Trading Volume") %>%
  layout(title = list(text = "Interactive Daily Trading Volume Plot for TLSA.US \
                      with EMA Lines and Trading Signals", 
                      x = 0.5, y = 0.95, 
                      xanchor = 'center', yanchor = 'top'),
         xaxis = list(title = "Date", type = "date", rangeslider = list(visible = TRUE),
                      rangeselector = list(
                        buttons = list(
                          list(count = 1, label = "1w", 
                               step = "week", stepmode = "backward"),
                          list(count = 2, label = "2w", 
                               step = "week", stepmode = "backward"),
                          list(count = 1, label = "1m", 
                               step = "month", stepmode = "backward"),
                          list(count = 6, label = "6m", 
                               step = "month", stepmode = "backward"),
                          list(count = 12, label = "TTM", 
                               step = "month", stepmode = "backward"),
                          list(count = 1, label = "YTD",
                               step = "year", stepmode = "todate"),
                          list(count = 1, label = "1y", 
                               step = "year", stepmode = "backward"),
                          list(step = "all")
                      )
                    )),
         yaxis = list(title = "Daily Trading Volume", fixedrange = FALSE, side = "left"),
         yaxis2 = list(title = "Daily EMA Values", 
                       overlaying = "y", side = "right", 
                       showgrid = FALSE,titlefont = list(size = 14)),
         barmode = 'group',
         legend = list(orientation = "h", x = 0.5, y = -0.4, 
                       xanchor = "center", yanchor = "top"),
         margin = list(l = 40, r = 40,b = 100, t = 100, pad = 4), height = 450)

vol_signal_colors <- c("BUY" = "lightgreen", "SELL" = "pink")
signals <- c("tsignal4", "tsignal5", "tsignal6")

for (sig in signals) {
  volume_plot <- volume_plot %>%
    add_markers(data = ema_signal_plot_html %>% 
                  filter(get(sig) == "BUY"), 
                x = ~date, y = ~volume, 
                marker = list(color = vol_signal_colors[["BUY"]], 
                              size = 10, symbol = "circle"),
                name = paste(sig, "BUY"),
                hoverinfo = "text",
                hovertemplate = paste("<b>Date:</b> %{x|%Y-%m-%d}<br><b>", 
                                      sig, "BUY</b><extra></extra>")) %>%
    add_markers(data = ema_signal_plot_html %>% filter(get(sig) == "SELL"), 
                x = ~date, y = ~volume, 
                marker = list(color = vol_signal_colors[["SELL"]], 
                              size = 10, symbol = "x"),
                name = paste(sig, "SELL"),
                hoverinfo = "text",
                hovertemplate = paste("<b>Date:</b> %{x|%Y-%m-%d}<br><b>", 
                                      sig, "SELL</b><extra></extra>"))
}

ema_lines <- c("EMA5", "EMA8", "EMA13", "EMA20", "EMA50", "EMA200")

ema_colors <- c("EMA5" = "black", "EMA8" = "yellow",
                "EMA13" = "purple", "EMA20" = "red", 
                "EMA50" = "grey", "EMA200" = "blue")

for (ema in ema_lines) {
  volume_plot <- 
    volume_plot %>%
    add_lines(data = ema_signal_plot_html, 
          x = ~date, y = as.formula(paste0("~", ema)), name = ema, 
              line = list(color = ema_colors[ema]), yaxis = "y2",
              hoverinfo = "y+text", 
              hovertemplate = paste("<b>Date:</b> %{x|%Y-%m-%d}<br><b>", 
                                    ema, ":</b> %{y:.2f}<extra></extra>"))
}

volume_plot
```

</br>

Output 3.3.d: Interactive **MACD** plot with trading signals on Volume, duration setting TTM.  

输出 3.3.d: 交互式**MACD**成交量图表，包括**MACD**策略交易信号，时间设置为TTM。 


</br>


### **MACD**总结 Summary- **MACD**:  

`In Progress`


The program is now constructed to generate **daily trading signals** given by the **Moving Average Convergence Divergence (MACD)** indicator values. The latest applied parameter settings and trading rules for the **EMA**-generated signals are summarized above. 

**Daily trading signals** from the **MACD** indicators, include `tsignal7`, `tsignal8` and `tsignal9`, for all stocks are generated; and the results (data tables and plots) for `AAPL.US` are shown above as illustrations, refer to the *webapp* for the complete data tables and plots/visualizations outputs.


根据**指数平滑移动平均线（MACD）**指标值给出**每日交易信号**的模型程序现已构建完成。选股模型最新应用的指标参数设定和**MACD**策略生成的交易信号的相关分析和设定已在上述部分总结。

**MACD**指标的**每日交易信号**，包括`tsignal7`,`tsignal8`和`tsignal9`，且已经为模型中所有的股票生成**每日交易信号**；并且以`苹果公司(AAPL.US)`的结果（数据表和图表）作为示例展示，完整图表可参阅*webapp*。 

$^*$ Whether the **MACD** indicator, or the trading signals `tsignal7`, `tsignal8` and `tsignal9` are effective in selecting stocks to construct a portfolio trading strategies with upsides, will be further analyzed by the model, and refer to **$\S 4.1$ ** [选取有效的技术指标（动态更新）Dynamic: Selecting Effective Technical Indicators] below for more details. 

$^*$ **MACD**指标或策略交易信号`tsignal7`,`tsignal8`和`tsignal9`在组合交易策略中是否具备有效选择上升潜力股票的能力，将由选股模型进一步分析，详情参考**$\S 4.1$ ** [选取有效的技术指标（动态更新）Dynamic: Selecting Effective Technical Indicators]。





<div style="text-align: right;">
**返回目录  **[快速索引 Quick Table of Contents] 
</div>




<!-- Disclaimer section with a gray bar -->
<div style="width: 100%; height: 20px; background-color: grey;"></div>

<!-- Disclaimer Text -->
<div style="padding: 20px; margin-top: 20px; background-color: #f1f1f1;">
    内部资料，请勿外传! 

    Internal documents, please do not disseminate! 

    本网页模型搭建说明及模型网络应用仅供参考。无论是所含信息还是所表达的观点，
    均不得明示或暗示为任何形式的建议、提供、招揽、邀请、广告、诱导、推荐或代表，
    以买卖任何证券、金融工具或任何投资或其他特定产品。

    The web-based Quantitative Model e-Manual and web application are for information
    purposes only. The information and opinion contained and expressed herein, shall not,
    and shall not be deemed to, construed, expressly or impliedly, as advice, offer or
    solicitation of an offer, invitation, advertisement, inducement, recommendation, or
    representation of any kind or form whatsoever to buy or sell any security, financial
    instrument or any investment or other specific product.
</div>










