## <span style="color:blue">技术指标4：相对强弱指数 Technical Indicator 4: Relative Strength Index (RSI)</span> 

Includes `tsignal10`, `tsignal11`, and `tsignal12`

包括交易信号 `tsignal10`, `tsignal11`, 以及 `tsignal12`  


```{r 304-98, message=FALSE, warning=FALSE, include=FALSE}
# Define function to read another rmd file
source_rmd <- function(file, local = FALSE, ...){
  options(knitr.duplicate.label = 'allow')

  tempR <- tempfile(tmpdir = ".", fileext = ".R")
  on.exit(unlink(tempR))
  knitr::purl(file, output=tempR, quiet = TRUE)

  envir <- globalenv()
  source(tempR, local = envir, ...)
}
```

```{r 304-99, message=FALSE, warning=FALSE, include=FALSE}
# Read in base model construction rmd to continue with 3.4
source_rmd("03_c_MACD.Rmd")
```


### **RSI**简介 Intro- **RSI**: 

`In Progress`

The **Relative Strength Index (RSI)** is a momentum oscillator that measures the speed and change of price movements. It ranges from 0 to 100 and is used to identify overbought or oversold conditions in a market. An RSI level below 30 generates buy signals while an RSI level above 70 generates sell signals.

Note: The exclusion of machine learning.
Technical. Example RSI Fundamental example ICIR to dig significant momentum factors.


Mathematically defined as: 数学上定义为：

Upward and downward indicators, $U_{t}$ and $D_{t}$, are

$$U_{t} = 
\begin{cases} 
P_{t}-P_{t-1}, & \text{if } P_{t} > P_{t-1} \\
0, & \text{if } P_{t} \leq P_{t-1}
\end{cases}$$

and

$$D_t = 
\begin{cases} 
0, & \text{if } P_{t} \geq P_{t-1} \\
P_{t-1}-P_{t}, & \text{if } P_{t} < P_{t-1}
\end{cases}$$

Then $\text{up}_t(N)$ and $\text{down}_t(N)$ are average numbers of upward moves and downward moves of closing price of past $n$ days:

If we use the **Simple Moving Average (SMA)**, then we have

$$\text{up}_t(N) = \frac{U_t + U_{t-1} + \ldots + U_{t-n+1}}{n}$$

and

$$\text{down}_t(N) = \frac{D_t + D_{t-1} + \ldots + D_{t-n+1}}{n}$$
Instead, we may use **Exponential Moving Average (EMA)**.  

Relative strength (RS) is relative ratio of days with upward moves and downward moves during last n days. Formally:  


$$\text{RS} = \frac{\text{up}_t(N)}{\text{down}_t(N)}$$

An $n$-day **RSI** is given by  

$$\text{RSI}_t(n) = 100 \frac{\text{RS}_{t}(n)}{1+\text{RS}_{t}(n)}$$  

where **RSI** is normalized relative strength.  

In calculation, we usually consider directly:

$$\text{RSI}_t(n) = 100 \frac{\text{up}_t(N)}{\text{up}_t(N)+\text{down}_t(N)}$$


`In Progress`

The program uses the formula above to compute the **Relative Strength Index (RSI)** values for **all stocks** in the model with various parameter settings, and creates appropriate related visualizations. The **RSI**-based **daily trading signals** will then be constructed from the subjectively set trading rules.  

`In Progress`

选股模型程序使用上述公式计算模型中**所有股票**的在多个不同的参数设定下的**相对强弱指数（RSI）**值，并创建相应的可视化图表。然后，根据主观设定的交易规则构建**RSI****日交易信号**。

```{r 304-1, echo=FALSE, message=FALSE, warning=FALSE}
# Define a function to compute the value for RSI using the adjusted close price with parameter settings of n days 

RSI_comput <- function (price,n){
  N <- length(price)
  U <- rep(0,N)
  D <- rep(0,N)
  rsi <- rep(NA,N)
  Lprice <- Lag(price,1)
  for (i in 2:N){
    if (price[i]>=Lprice[i]){
      U[i] <- price[i]- Lprice[i]
    } else{
      D[i] <- Lprice[i]- price[i]
    }
    if (i>n){
      AvgUp <- mean(U[(i-n+1):i])
      AvgDn <- mean(D[(i-n+1):i])
      rsi[i] <- AvgUp/(AvgUp+AvgDn)*100 
      }
    }
  rsi <- reclass(rsi, price)
  return(rsi)
}
```

```{r 304-2, message=FALSE, warning=FALSE, include=FALSE}
# Compute RSI for all stocks, Full Data
mega7data_modified <-
  mega7data_modified %>%
  group_by(symbol) %>%
  mutate(RSI9 = RSI_comput(adjusted, 9),
         RSI14 = RSI_comput(adjusted, 14),
         RSI25 = RSI_comput(adjusted, 25))
```

```{r 304-3, message=FALSE, warning=FALSE, include=FALSE}
# Alternative way: 
# Below utilizes the `TTR` package directly for RSI computations: RSI()
# AAPL <- xts(rsi_value_result_pdf$adjusted,rsi_value_result_pdf$date)
# rsi <- RSI(AAPL,SMA, n = 14) 
```

```{r 304-4, message=FALSE, warning=FALSE, include=FALSE}
rsi_value_result <- 
  mega7data_modified %>%
  mutate(date = as.Date(date)) %>%
  select(date, adjusted, RSI9, RSI14, RSI25, volume) %>%
  arrange(desc(date)) %>%
  head(5000)

rsi_value_result_pdf <- 
  mega7data_modified %>%
  slice(which(symbol == "AAPL")) %>%
  mutate(date = as.Date(date)) %>%
  select(date, adjusted, RSI9, RSI14, RSI25, volume) %>%
  arrange(desc(date))
```

```{r 304-5, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}

# NOT FINISHED 

# ##### [Code Hidden 代码已隐藏]{style="color:red"} {-}

# ##### [Individual stock outputs are suppressed, only `AAPL.US` related results are shown for illustration purposes. Refer to the *webapp* or the `html` version of the *e-Manual* for complete outputs. 个股输出数据及图表已隐藏，报告仅展示`苹果公司(AAPL.US)`的相关结果,完整图表可参阅*webapp* 或网页版*Global MAS 量化模型搭建说明*。]{style="color:red"} {-}

# pdf output
# Display AAPL output (EMA values)
kbl(head(ema_value_result_pdf,10), booktabs = T, linesep = '', digits = 1,
    caption = "EMA Computations for AAPL.US",
    format.args = list(big.mark = ",", scientific = FALSE),
    col.names = c("Symbol","Date","Adj Close","EMA5","EMA8",
                  "EMA13","EMA20","EMA50","EMA200","Volume")) %>%
  kable_styling(latex_options = c("striped", "scale_down",
                                  "HOLD_position"), 
                position = "center") %>%
  column_spec(c(1,4:9), bold = T) %>%
  kableExtra::footnote(general = "Output 3.2.a: Latest 10 rows of data are shown.")
```

##### [Code Hidden 代码已隐藏]{style="color:red"} {-}

##### [Enter the ticker/symbol in the search box for stock-specific results. Sort tool is available next to the variable names. 搜索框中输入股票代码可以过滤展示个股相关结果。点击变量名旁的箭头可进行排序。]{style="color:purple"} {-}

```{r 304-6, echo=FALSE, message=FALSE, warning=FALSE}
# html output
# Display RSI values
DT::datatable(rsi_value_result, 
              colnames = c('Symbol' = 2, 'Date' = 3, 'Adjusted' = 4, 
                           'RSI(9)' = 5, 'RSI(14)' = 6, 'RSI(25)' = 7, 
                           'Volume' = 8),
              caption = htmltools::tags$caption(style = 'caption-side: top; 
                                            text-align: center; color: black; 
                                            font-size: 200%;',
                                            'RSI Computations'),
              options = list(pageLength = 10, lengthMenu = c(5, 10, 15, 20),
              searching = TRUE, style = list(width = '100%')), 
              extensions = 'Buttons') %>%
  formatRound(columns = c('Adjusted','RSI(9)', 'RSI(14)', 'RSI(25)'), 
              digits = 2)  %>%
  formatRound(columns = 'Volume', digits = 0)
```

Output 3.4.a: **RSI** Computations, latest 10 rows of data are shown.  

图表 3.4.a: **RSI** 计算结果，展示最新的 10 行数据。

</br>

The program computed the **RSI** values for all stocks input in the model, with the parameter settings of $n=9, 14, 25$. As an illustration, above table shows the computed **RSI** values and plots (end of section). 

模型程序为输入的所有股票计算了**RSI**值，参数设定为$n=9,14,25$。作为示例，上表展示了计算的**EMA**值并创建了可视化图表（节末）。

```{r 304-7, message=FALSE, warning=FALSE, include=FALSE}
# Data manipulation for RSI plot AAPL.US
rsi_aapl_xts <- 
  mega7data_modified %>%
  slice(which(symbol == "AAPL")) %>%
  mutate(date = as.POSIXct(date)) %>%
  select(date, open, high, low, close, volume, adjusted) %>%
  na.omit()

open <- rsi_aapl_xts$open
high <- rsi_aapl_xts$high
low <- rsi_aapl_xts$low
close <- rsi_aapl_xts$close
adjusted <- rsi_aapl_xts$adjusted
volume <- as.numeric(rsi_aapl_xts$volume)

rsi_aapl_xts <- xts(cbind(open, high, low, close, volume, adjusted),
                   as.POSIXct(rsi_aapl_xts$date))
rsi_aapl_xts <- last(rsi_aapl_xts,'365 days')
```

```{r 304-8, message=FALSE, warning=FALSE, include=FALSE}
##### AAPL Plot include RSI(14) using `TTR` package {-}
# pdf plot
# RSI plot TLSA.US RSI(14)
chartSeries(rsi_aapl_xts,
            type = "candlesticks",
            theme = chartTheme('black'))
addRSI(n = 14,maType = "SMA")
```


### 交易信号与策略- **RSI** Trading signal(s) & strategies- **RSI**:



`In Progress`

```{r eval=FALSE, include=FALSE}
RSI（Relative Strength Index，相对强弱指数）是一种动量振荡器，用于评估一项资产的过度买入或过度卖出状态。RSI 的值范围为0到100，通常用14天周期计算。
RSI 指标的计算公式如下：

其中：
pos_avg是价格上升时的价格变化的滚动平均值，反映了近期的平均正向价格变化。
neg_avg是价格下降时的价格变化的滚动平均值，反映了近期的平均负向价格变化。
RSI 的使用方法：
1）超买或超卖：当 RSI 从高于70的区域下降，通常被认为是过度买入状态，可能预示着未来价格将下跌。相反，当 RSI 从低于30的区域上升，通常被认为是过度卖出状态，可能预示着未来价格将上涨。
2）背离：当价格创新高或新低，而 RSI 没有相应地创新高或新低，可能出现所谓的“背离”，此时可能预示着价格的反转。
3）中线交叉：如果 RSI 从下方向上穿过 50，可能预示着市场情绪从悲观转向乐观，可能是买入信号。反之，如果 RSI 从上方向下穿过 50，可能预示着市场情绪从乐观转向悲观，可能是卖出信号。



The Relative Strength Index (RSI) is a popular momentum oscillator in technical analysis, and there are several common trading rules or signals associated with its movements. These rules are based on the RSI crossing certain threshold levels, divergences with price, and specific patterns within the RSI itself. Here's a breakdown of some widely used RSI trading rules:

### 1. Overbought and Oversold Signals
- **Overbought Signal**: When the RSI crosses above 70, it suggests that the asset may be getting overbought and could be due for a correction or pullback. Traders might consider this a signal to sell or take profits.
- **Oversold Signal**: Conversely, when the RSI crosses below 30, it indicates that the asset may be oversold and potentially undervalued, which could lead to a rebound. This is often taken as a buy signal by traders.

### 2. Centerline Crossover
- **Bullish Signal**: An RSI moving from below 50 to above 50 indicates increasing bullish momentum. This is considered a bullish signal, suggesting that the price might continue to rise.
- **Bearish Signal**: When the RSI moves from above 50 to below 50, it indicates increasing bearish momentum. Traders might take this as a signal that the price could continue to fall.

### 3. RSI Divergence
- **Bullish Divergence**: Occurs when the price records a lower low, but the RSI forms a higher low. This indicates weakening downward momentum and a potential bullish reversal.
- **Bearish Divergence**: Happens when the price records a higher high, but the RSI forms a lower high. This signals weakening upward momentum and a potential bearish reversal.

### 4. Swing Rejections
- **Bullish Swing Rejection**: It has four parts: (a) the RSI falls into the oversold area (below 30), (b) the RSI crosses back above 30, (c) a pullback within the oversold area without crossing below 30 again, and (d) the RSI then breaks its most recent high. This sequence suggests a strong bullish reversal.
- **Bearish Swing Rejection**: This signal includes: (a) the RSI rises into the overbought area (above 70), (b) the RSI crosses back below 70, (c) a rally back into the overbought area without crossing above 70 again, and (d) the RSI then breaks its most recent low. It suggests a bearish reversal.

### 5. Trendline Breaks within the RSI
- **Bullish Signal**: Drawing trendlines directly on the RSI chart and seeing the RSI break above a downtrend line can signal a bullish reversal.
- **Bearish Signal**: Conversely, if the RSI breaks below an uptrend line drawn on the RSI chart, it can be a bearish reversal signal.

It's important for traders to use these RSI signals in conjunction with other technical analysis tools and indicators to confirm trading signals and strategies. Also, considering the asset's volatility, market conditions, and adjusting RSI settings (like the period length) can help tailor the use of RSI to individual trading preferences and strategies.
```

### **RSI**策略交易信号汇总 To summarize for **RSI** trading signals: 


-   **RSI**- `tsignal10`:\
    **BUY**: $\text{RSI}$ cross from **below 30 to above 30**,\
    **SELL**: $\text{RSI}$ cross from **above 70 to below 70**, \
    **HOLD**: otherwise;  
    
- **RSI**交易信号- `tsignal10`:\
    **买入**: $\text{RSI}$ **从30下方穿越至30的上方**,\
    **卖出**: $\text{RSI}$ **从70上方穿越至70的下方**,\
    **持有**: 其他情况;   
    
`In Progress` 
Swing Rejections    

-   **RSI**- `tsignal11`:\
    **BUY**:After an initial $\text{RSI}$ cross from below 30 to above 30, if the minimum $\text{RSI}$ value remains above 30 for the next 5 days,\
    **SELL**: After an initial $\text{RSI}$ cross from above 70 to below 70, if the maximum $\text{RSI}$ value remains below 70 for the next 5 days, \
    **HOLD**: otherwise;  
    
- **RSI**交易信号- `tsignal11`:\
    **买入**: 初始$\text{RSI}$从30下方穿越至30上方之后，如果在接下来的5天内最小$\text{RSI}$值保持在30以上,\
    **卖出**: 初始$\text{RSI}$从70上方穿越至70下方之后，如果在接下来的5天内最大$\text{RSI}$值保持在70以下,\
    **持有**: 其他情况;   
    
-   **RSI**- `tsignal12`:\
    **BUY**: $\text{RSI}$ cross from **below 50 to above 50**,\
    **SELL**: $\text{RSI}$ cross from **above 50 to below 50**, \
    **HOLD**: otherwise;  
    
- **RSI**交易信号- `tsignal12`:\
    **买入**: $\text{RSI}$ **从50下方穿越至50的上方**,\
    **卖出**: $\text{RSI}$ **从50上方穿越至50的下方**,\
    **持有**: 其他情况;

```{r 304-9, message=FALSE, warning=FALSE, include=FALSE}
# RSI Trading Signal 10: RSI crossover 30, 70 
# RSI Trading Rule setup and Generate Signals 

mega7data_modified <- 
  mega7data_modified %>%
  group_by(symbol) %>%
  mutate(tsignal10 = case_when(
    lag(RSI14) < 30 & RSI14 >= 30 ~ 'BUY',
    lag(RSI14) > 70 & RSI14 <= 70 ~ 'SELL',
    TRUE ~ 'HOLD'))
```

```{r 304-10, message=FALSE, warning=FALSE, include=FALSE}
# RSI Trading Signal 11: RSI Swing Rejections on 30, 70  
# RSI Trading Rule setup and Generate Signals 

mega7data_modified <- 
  mega7data_modified %>%
  group_by(symbol) %>%
  mutate(
    initial_bullish = lag(RSI14) < 30 & RSI14 >= 30,
    initial_bearish = lag(RSI14) > 70 & RSI14 <= 70,
    retest_bullish = ifelse(initial_bullish, lag(RSI14, 5) >= 30, FALSE),
    retest_bearish = ifelse(initial_bearish, lag(RSI14, 5) <= 70, FALSE),
    tsignal11 = 
      case_when(
      initial_bullish & retest_bullish ~ 'BUY',
      initial_bearish & retest_bearish ~ 'SELL',
      TRUE ~ 'HOLD')
    ) %>% 
  select(-initial_bullish, -initial_bearish, -retest_bullish, -retest_bearish)
  
```

```{r 304-11, message=FALSE, warning=FALSE, include=FALSE}
# RSI Trading Signal 12: RSI crossover 50
# RSI Trading Rule setup and Generate Signals 

mega7data_modified <- 
  mega7data_modified %>%
  group_by(symbol) %>%
  mutate(tsignal12 = case_when(
    lag(RSI14) < 50 & RSI14 > 50 ~ 'BUY',
    lag(RSI14) >= 50 & RSI14 < 50 ~ 'SELL',
    TRUE ~ 'HOLD')) 
```

```{r 304-12, message=FALSE, warning=FALSE, include=FALSE, paged.print=TRUE}
# Prepare data frame RSI signal results
rsi_signal_result <-
  mega7data_modified %>%
  select(date, symbol, adjusted, tsignal10, 
         tsignal11, tsignal12) %>%
  arrange(desc(date)) %>%
  head(5000)

# For AAPL signals results (RSI)
rsi_signal_result_pdf <-
  mega7data_modified %>%
  slice(which(symbol == "AAPL")) %>%
  ungroup() %>%
  select(date, symbol, adjusted, tsignal10, 
         tsignal11, tsignal12) %>%
  arrange(desc(date))
```

```{r 304-13, eval=FALSE, fig.pos='H', message=FALSE, warning=FALSE, include=FALSE}

# NOT FINISHED 

# ##### [Code Hidden 代码已隐藏]{style="color:red"} {-}

# ##### [Individual stock outputs are suppressed, only `AAPL.US` related results are shown for illustration purposes. Refer to the *webapp* or the `html` version of the *e-Manual* for complete outputs. 个股输出数据及图表已隐藏，报告仅展示`苹果公司(AAPL.US)`的相关结果,完整图表可参阅*webapp* 或网页版*Global MAS 量化模型搭建说明*。]{style="color:red"} {-}

# pdf output
# Display AAPL signal results (EMA signals)
kbl(head(ema_signal_result_pdf,10), booktabs = T, linesep = "", longtable = T, 
    digits = 1, caption = "EMA Trading Signals for AAPL.US", 
    format.args = list(big.mark = ",", scientific = FALSE),
    col.names = c("Date","Symbol","Adj Close","tsignal4","tsignal5",
                  "tsignal6","tsignal6a","tsignal6b")) %>%
  kable_styling(latex_options = c("striped", "scale_up",
                                  "HOLD_position"),
                full_width = F) %>%
  column_spec(c(2,4:6), bold = T) %>%
  column_spec(1, width = "1.9cm") %>%
  kableExtra::footnote(general = "Output 3.2.b: latest 10 rows of data are shown.",
              number = "Includes tsignal4, tsignal5, tsignal6, tsignal6a and tsignal6b.")
#图表3.2.b: EMA交易信号，展示最新的10行数据。包括`tsignal4`, `tsignal5`, `tsignal6`, #`tsignal6a`和`tsignal6b`。
```

##### [Code Hidden 代码已隐藏]{style="color:red"} {-}

##### [Enter the ticker/symbol in the search box for stock-specific results. Sort tool is available next to the variable names. 搜索框中输入股票代码可以过滤展示个股相关结果。点击变量名旁的箭头可进行排序。]{style="color:purple"} {-}

```{r 304-14, echo=FALSE, message=FALSE, warning=FALSE}
# html output
# Display RSI signal results 
DT::datatable(rsi_signal_result, 
              colnames = c('Date' = 2, 'Symbol' = 3, 'Adjusted' = 4,
                           'Signal 10' = 5, 'Signal 11' = 6, 'Signal 12' = 7),
              caption = htmltools::tags$caption(style = 'caption-side: top; 
                                            text-align: center; color: black; 
                                            font-size: 200%;',
                                            'RSI Trading Signals'),
              options = list(pageLength = 10, lengthMenu = c(5, 10, 15, 20),
              searching = TRUE, style = list(width = '100%')), 
              extensions = 'Buttons') %>%
    formatRound(columns = 'Adjusted', digits = 2)  
```

Output 3.4.b: **RSI** trading signals, latest 10 rows of data are shown. Includes `tsignal10`, `tsignal11`, and `tsignal12`.  

图表3.4.b: **RSI**交易信号，展示最新的10行数据。包括`tsignal10`, `tsignal11`, 和`tsignal12`。

```{r 304-15, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}

# NOT FINISHED 

# pdf output
# EMA Candlestick+Volume Plot for AAPL with trading signals
# Prepare the dataset for candlestick components
ema_signal_plot_pdf<- 
  mega7data_modified %>%
  slice(which(symbol == "AAPL")) %>%
  select(date, symbol, adjusted, open, close, high, low, volume, EMA5, 
         EMA8, EMA13, EMA20, EMA50, EMA200, tsignal4, tsignal5, tsignal6) %>%
  mutate(date = as.Date(date, format = "%Y-%m-%d"),
         day_trend_color = ifelse(open - adjusted > 0, "red", "green")) %>%
  filter(as.Date(date) > as.Date(Sys.Date()-months(12)))
```

```{r 304-16, eval=FALSE, fig.height=7, fig.width=10, message=FALSE, warning=FALSE, include=FALSE}

# NOT FINISHED 

# pdf output
# EMA Candlestick+Volume Plot for AAPL with trading signals

# Candlestick Plot with EMA Trading Signals
color_values <- c(
  "EMA5" = "black", 
  "EMA8" = "yellow", 
  "EMA13" = "purple", 
  "EMA20" = "red", 
  "EMA50" = "grey", 
  "EMA200" = "blue",
  "green" = "darkgreen", 
  "red" = "red",
  "Signal4 BUY " = "lightgreen", 
  "Signal4 SELL" = "deeppink",
  "Signal5 BUY" = "lightgreen", 
  "Signal5 SELL" = "deeppink",
  "Signal6 BUY" = "lightgreen", 
  "Signal6 SELL" = "deeppink"
)

candlestick <- 
  ggplot(ema_signal_plot_pdf, aes(x = date)) +
  geom_segment(aes(xend = date, y = open, 
                   yend = adjusted, colour = day_trend_color), size = 5) +
  geom_segment(aes(xend = date, y = high, 
                   yend = low, colour = day_trend_color)) +
  geom_line(aes(y = EMA5, color = "EMA5"), size = 0.5) +
  geom_line(aes(y = EMA8, color = "EMA8"), size = 0.5) +
  geom_line(aes(y = EMA13, color = "EMA13"), size = 0.5) +
  geom_line(aes(y = EMA20, color = "EMA20"), size = 0.5) +
  geom_line(aes(y = EMA50, color = "EMA50"), size = 0.5) +
  geom_line(aes(y = EMA200, color = "EMA200"), size = 0.5) +

  # Adding trading signals with different shapes and colors
  geom_point(data = filter(ema_signal_plot_pdf, tsignal4 == "BUY"),
             aes(x = date, y = high, color = "Signal4 BUY", 
                 shape = "Signal4 BUY"), size = 2) +
  geom_point(data = filter(ema_signal_plot_pdf, tsignal4 == "SELL"), 
             aes(x = date, y = low, color = "Signal4 SELL", 
                 shape = "Signal4 SELL"), size = 2) +
  geom_point(data = filter(ema_signal_plot_pdf, tsignal5 == "BUY"), 
             aes(x = date, y = high, color = "Signal5 BUY", 
                 shape = "Signal5 BUY"), size = 2) +
  geom_point(data = filter(ema_signal_plot_pdf, tsignal5 == "SELL"), 
             aes(x = date, y = low, color = "Signal5 SELL", 
                 shape = "Signal5 SELL"), size = 2) +
  geom_point(data = filter(ema_signal_plot_pdf, tsignal6 == "BUY"), 
             aes(x = date, y = high, color = "Signal6 BUY", 
                 shape = "Signal6 BUY"), size = 2) +
  geom_point(data = filter(ema_signal_plot_pdf, tsignal6 == "SELL"), 
             aes(x = date, y = low, color = "Signal6 SELL", 
                 shape = "Signal6 SELL"), size = 2) +
  theme(legend.position = "top",
            guides(color = guide_legend(nrow = 4, byrow = TRUE, 
                                title = "Indicators & Signals"), 
    shape = guide_legend(nrow = 4, byrow = TRUE, title = "Trade Signals") 
  )) +
  scale_color_manual(name = "Indicators & Signals", values = color_values) +
  scale_shape_manual(name = "Signal Shapes", 
                     values = c("Signal4 BUY" = 17, "Signal4 SELL" = 4, 
                                "Signal5 BUY" = 18, "Signal5 SELL" = 3, 
                                "Signal6 BUY" = 15, "Signal6 SELL" = 1)) +
  labs(
    y = "Stock Price, in USD", x = "Date") +
    labs(title = paste0("Price Volume Candlestick Plot for TLSA.US \
       with EMA Lines and Trading Signals")) +
  theme_bw() +
  scale_x_date(date_breaks = "2 months", date_labels = "%b %Y")

# Volume Plot
volume_plot <- 
  ggplot(ema_signal_plot_pdf, aes(x = date, y = volume, fill = day_trend_color)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = c("green" = "darkgreen", "red" = "red")) +
  labs(y = "Daily Trading Volume", x = "Date") +
  theme_bw() +
  theme(legend.position = "none",
            guides(color = guide_legend(nrow = 4, byrow = TRUE, 
                                title = "Indicators & Signals"), 
    shape = guide_legend(nrow = 4, byrow = TRUE, title = "Trade Signals") 
  )) +
  scale_x_date(date_breaks = "2 months", date_labels = "%b %Y") +
  scale_y_continuous(labels = scales::comma)


# Combine 2 plots
ggarrange(candlestick, volume_plot, ncol = 1, nrow = 2,
    heights =c(9,3), widths = 10, align = "v") 

# Output 3.1.c: EMA plot with trading signals on Price and Volume, duration setting TTM.
```

```{r 304-17, echo=FALSE, message=FALSE, warning=FALSE}
# html output
# plotly interactive plot
# RSI Candlestick Plot + RSI subplot for AAPL with trading signals
# Prepare the dataset 

rsi_signal_plot_html<- 
  mega7data_modified %>%
  slice(which(symbol == "AAPL")) %>%
  select(date, symbol, adjusted, open, close, high, low, volume, RSI9, 
         RSI14, RSI25, tsignal10, tsignal11, tsignal12) %>%
  mutate(date = as.Date(date, format = "%Y-%m-%d"),
         day_trend_color =  ifelse(open < adjusted, "lightgreen", "red"),
         prev_volume = lag(volume),
         prev_adjusted = lag(adjusted),
         prev_RSI9 = lag(RSI9),
         prev_RSI14 = lag(RSI14),
         prev_RSI25 = lag(RSI25),
         volume_color = ifelse(volume > prev_volume, "orange", "lightblue"),
         hover_text_volume = paste(
      "<b>Symbol:</b>", symbol, "<br>",
      "<b>Date:</b>", format(date, '%Y-%m-%d'), "<br>",
      "<b>Daily Volume:</b>", formatC(volume, big.mark = ","),
      "<span style='color:", 
      ifelse(volume > prev_volume, "darkgreen", "red"), ";'>",
      ifelse(volume > prev_volume, "▲", "▼"), "</span>", "<br>")) %>% 
  filter(as.Date(date) > as.Date(Sys.Date()-months(12)))

# Define shapes for each signal
signal_shapes <- list(
  "Signal10 BUY" = "circle",
  "Signal10 SELL" = "circle-open",
  "Signal11 BUY" = "triangle-up",
  "Signal11 SELL" = "triangle-down-open",
  "Signal12 BUY" = "diamond",
  "Signal12 SELL" = "diamond-open"
)

rsi_signal_plot_html <- 
  rsi_signal_plot_html %>%
  mutate(hover_text = paste(
    "<b>Symbol:</b>", symbol, "<br>",
    "<b>Date:</b>", format(date, '%Y-%m-%d'), "<br>",
    "<b>Adjusted Close Price:</b> $", round(adjusted, 2), "<br>",
    "<span style='color:", 
    ifelse(adjusted > prev_adjusted, "darkgreen", "pink"), ";'>",
      ifelse(adjusted > prev_adjusted, "▲", "▼"), "</span>", "<br>",
    "<b>Open:</b> $", round(open, 2), "<br>",
    "<b>High:</b> $", round(high, 2), "<br>",
    "<b>Low:</b> $", round(low, 2), "<br>",
    "<b>Volume:</b>", formatC(volume, format = "f", big.mark = ","),
     "<span style='color:", 
      ifelse(volume > prev_volume, "darkgreen", "red"), ";'>",
      ifelse(volume > prev_volume, "▲", "▼"), "</span>", "<br>"
  )) 

# Hover for RSI subplot
rsi_signal_plot_html <- 
  rsi_signal_plot_html %>%
  mutate(hover_text_rsi = paste(
      "<b>Symbol:</b>", symbol, "<br>", 
      "<b>Date:</b>", format(date, '%Y-%m-%d'), "<br>",
      "<b>Adjusted Close Price:</b> $", round(adjusted, 2), 
      "<span style='color:", 
      ifelse(adjusted > prev_adjusted, "darkgreen", "red"), ";'>",
      ifelse(adjusted > prev_adjusted, "▲", "▼"), "</span>", "<br>",
      "<b>RSI(9):</b>", round(RSI9, 2),
      "<span style='color:", 
      ifelse(RSI9 > prev_RSI9, "darkgreen", "deeppink"), ";'>",
      ifelse(RSI9 > prev_RSI9, "▲", "▼"), "</span>", "<br>",
      "<b>RSI(14):</b>", round(RSI14, 2),
      "<span style='color:", 
      ifelse(RSI14 > prev_RSI14, "darkgreen", "deeppink"), ";'>",
      ifelse(RSI14 > prev_RSI14, "▲", "▼"), "</span>", "<br>",
      "<b>RSI(25)</b>", round(RSI25, 2),
      "<span style='color:", 
      ifelse(RSI25 > prev_RSI25, "darkgreen", "deeppink"), ";'>",
      ifelse(RSI25 > prev_RSI25, "▲", "▼"), "</span>", "<br>"
    )
  )
```

##### [Code Hidden 代码已隐藏]{style="color:red"} {-}

##### [Individual stock outputs are suppressed, only `AAPL.US` related results are shown for illustration purposes. Refer to the *webapp* for the complete plot output. 个股输出数据及图表已隐藏，报告仅展示`苹果公司(AAPL.US)`的相关结果,完整图表可参阅*webapp*。]{style="color:red"} {-}

```{r 304-18, echo=FALSE, fig.height=7, fig.width=12, message=FALSE, warning=FALSE}
# html output
# plotly interactive plot
# RSI Candlestick Plot + RSI subplot for AAPL with trading signals

# Candlestick Plot with RSI Trading Signals
fig <- plot_ly(data = rsi_signal_plot_html, 
               type = "candlestick", 
               x = ~date, open = ~open, close = ~adjusted, 
               high = ~high, low = ~low,
               increasing = list(line = list(color = "darkgreen", width = 10), 
                                 fillcolor = "darkgreen"),
               decreasing = list(line = list(color = "red", width = 10), 
                                 fillcolor = "red"), 
               hoverinfo = "text", text = ~hover_text, showlegend = FALSE) %>%
  add_markers(data = filter(rsi_signal_plot_html, tsignal10 == "BUY"), 
              x = ~date, y = ~high, 
              marker = list(color = "lightgreen", size = 6,
                            symbol = signal_shapes[["Signal10 BUY"]]), 
              name = "Signal10 BUY", showlegend = TRUE,
              hoverinfo = "text",
              hovertemplate = 
                "<b>Date:</b> %{x|%Y-%m-%d}<br><b>Signal10 BUY</b><extra></extra>") %>%
  add_markers(data = filter(rsi_signal_plot_html, tsignal10 == "SELL"), 
              x = ~date, y = ~low, 
              marker = list(color = "pink", size = 6,
                            symbol = signal_shapes[["Signal10 SELL"]]), 
              name = "Signal10 SELL", showlegend = TRUE,
              hoverinfo = "text",
              hovertemplate = 
                "<b>Date:</b> %{x|%Y-%m-%d}<br><b>Signal10 SELL</b><extra></extra>") %>%
  add_markers(data = filter(rsi_signal_plot_html, tsignal11 == "BUY"), 
              x = ~date, y = ~high, 
              marker = list(color = "lightgreen", size = 6,
                            symbol = signal_shapes[["Signal11 BUY"]]), 
              name = "Signal11 BUY",  showlegend = TRUE,
              hoverinfo = "text",
              hovertemplate = 
                "<b>Date:</b> %{x|%Y-%m-%d}<br><b>Signal11 BUY</b><extra></extra>") %>%
  add_markers(data = filter(rsi_signal_plot_html, tsignal11 == "SELL"), 
              x = ~date, y = ~low, 
              marker = list(color = "pink", size = 6,
                            symbol = signal_shapes[["Signal11 SELL"]]), 
              name = "Signal11 SELL", showlegend = TRUE,
              hoverinfo = "text",
              hovertemplate = 
                "<b>Date:</b> %{x|%Y-%m-%d}<br><b>Signal11 SELL</b><extra></extra>") %>%
  add_markers(data = filter(rsi_signal_plot_html, tsignal12 == "BUY"), 
              x = ~date, y = ~high, 
              marker = list(color = "lightgreen", size = 6,
                            symbol = signal_shapes[["Signal12 BUY"]]), 
              name = "Signal12 BUY", showlegend = TRUE,
              hoverinfo = "text",
              hovertemplate = 
                "<b>Date:</b> %{x|%Y-%m-%d}<br><b>Signal12 BUY</b><extra></extra>") %>%
  add_markers(data = filter(rsi_signal_plot_html, tsignal12 == "SELL"), 
              x = ~date, y = ~low, 
              marker = list(color = "pink", size = 6,
                            symbol = signal_shapes[["Signal12 SELL"]]), 
              name = "Signal12 SELL", showlegend = TRUE,
              hoverinfo = "text",
              hovertemplate = 
                "<b>Date:</b> %{x|%Y-%m-%d}<br><b>Signal12 SELL</b><extra></extra>")

# Add the RSI9, RSI14, RSI25 lines on the same subplot as the histogram
fig <- fig %>%
  add_trace(
    data = rsi_signal_plot_html,
    x = ~date,
    y = ~RSI9,
    type = 'scatter',
    mode = 'lines',
    line = list(color = 'darkgrey'),
    name = 'RSI(9)',
    yaxis = 'y2', 
    showlegend = TRUE,
    hover_info = 'text',
    text = ~hover_text_rsi) %>%
  add_trace(
    data = rsi_signal_plot_html,
    x = ~date,
    y = ~RSI14,
    type = 'scatter',
    mode = 'lines',
    line = list(color = 'red'),
    name = 'RSI(14)',
    yaxis = 'y2',
    showlegend = TRUE,
    hover_info = 'text',
    text = ~hover_text_rsi) %>% 
  add_trace(
    data = rsi_signal_plot_html,
    x = ~date,
    y = ~RSI25,
    type = 'scatter',
    mode = 'lines',
    line = list(color = 'lightblue'),
    name = 'RSI(25)',
    yaxis = 'y2',
    showlegend = TRUE,
    hover_info = 'text',
    text = ~hover_text_rsi)
  

# Update the layout for the secondary y-axis without using 'overlaying' and set the domain for both y-axes
fig <- fig %>%
  layout(
    title = list(text = "Interactive Price Candlestick Plot for AAPL.US \
                      with RSI Subplot and Trading Signals",
                      x = 0.5,  
                      y = 1.2,  
                      xanchor = 'center',
                      yanchor = 'top'),
    yaxis = list(domain = c(0.4, 1), title = "Stock Price, in USD", fixedrange = FALSE),
    yaxis2 = list(domain = c(0, 0.25), title = "RSI", anchor = 'x', 
                  side = 'left', overlaying = NULL, fixedrange = FALSE),
    xaxis = list(domain = c(0, 1), title = "Date", anchor = 'y',
                      type = "date", 
                      rangeslider = list(visible = TRUE),
                      rangeselector = list(
                        buttons = list(
                          list(count = 1, label = "1w", 
                               step = "week", stepmode = "backward"),
                          list(count = 2, label = "2w", 
                               step = "week", stepmode = "backward"),
                          list(count = 1, label = "1m", 
                               step = "month", stepmode = "backward"),
                          list(count = 6, label = "6m", 
                               step = "month", stepmode = "backward"),
                          list(count = 12, label = "TTM", 
                               step = "month", stepmode = "backward"),
                          list(count = 1, label = "YTD",
                               step = "year", stepmode = "todate"),
                          list(count = 1, label = "1y", 
                               step = "year", stepmode = "backward"),
                          list(step = "all")
                      )
                    )),
    legend = list(orientation = "h",x = 0, y = -0.5, 
                       xanchor = "left", yanchor = "top", traceorder = "normal"),
    margin = list(t = 100, b = 200),
    width = 900, height = 750
  )

fig
```

Output 4.3.c: Interactive **RSI** plot with trading signals on Price, duration setting TTM.  

图表 4.3.c: 交互式**RSI**股价图表，包括**RSI**策略交易信号，时间设置为TTM。

##### [Code Hidden 代码已隐藏]{style="color:red"} {-}

##### [Individual stock outputs are suppressed, only `AAPL.US` related results are shown for illustration purposes. Refer to the *webapp* for the complete plot output. 个股输出数据及图表已隐藏，报告仅展示`苹果公司(AAPL.US)`的相关结果,完整图表可参阅*webapp*。]{style="color:red"} {-}

```{r 304-19, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}

# NOT FINISHED

# html output
# plotly interactive plot
# RSI Volume Plot for AAPL with trading signals
# Define signal colors and shapes for trading signals

volume_plot <- plot_ly(data = ema_signal_plot_html, 
                       x = ~date, y = ~volume, type = 'bar', 
                       marker = list(color = ~volume_color),
                       hoverinfo = 'text', text = ~hover_text_volume,
                       name = "Trading Volume") %>%
  layout(title = list(text = "Interactive Daily Trading Volume Plot for TLSA.US \
                      with EMA Lines and Trading Signals", 
                      x = 0.5, y = 0.95, 
                      xanchor = 'center', yanchor = 'top'),
         xaxis = list(title = "Date", type = "date", rangeslider = list(visible = TRUE),
                      rangeselector = list(
                        buttons = list(
                          list(count = 1, label = "1w", 
                               step = "week", stepmode = "backward"),
                          list(count = 2, label = "2w", 
                               step = "week", stepmode = "backward"),
                          list(count = 1, label = "1m", 
                               step = "month", stepmode = "backward"),
                          list(count = 6, label = "6m", 
                               step = "month", stepmode = "backward"),
                          list(count = 12, label = "TTM", 
                               step = "month", stepmode = "backward"),
                          list(count = 1, label = "YTD",
                               step = "year", stepmode = "todate"),
                          list(count = 1, label = "1y", 
                               step = "year", stepmode = "backward"),
                          list(step = "all")
                      )
                    )),
         yaxis = list(title = "Daily Trading Volume", fixedrange = FALSE, side = "left"),
         yaxis2 = list(title = "Daily EMA Values", 
                       overlaying = "y", side = "right", 
                       showgrid = FALSE,titlefont = list(size = 14)),
         barmode = 'group',
         legend = list(orientation = "h", x = 0.5, y = -0.4, 
                       xanchor = "center", yanchor = "top"),
         margin = list(l = 40, r = 40,b = 100, t = 100, pad = 4), height = 450)

vol_signal_colors <- c("BUY" = "lightgreen", "SELL" = "pink")
signals <- c("tsignal4", "tsignal5", "tsignal6")

for (sig in signals) {
  volume_plot <- volume_plot %>%
    add_markers(data = ema_signal_plot_html %>% 
                  filter(get(sig) == "BUY"), 
                x = ~date, y = ~volume, 
                marker = list(color = vol_signal_colors[["BUY"]], 
                              size = 10, symbol = "circle"),
                name = paste(sig, "BUY"),
                hoverinfo = "text",
                hovertemplate = paste("<b>Date:</b> %{x|%Y-%m-%d}<br><b>", 
                                      sig, "BUY</b><extra></extra>")) %>%
    add_markers(data = ema_signal_plot_html %>% filter(get(sig) == "SELL"), 
                x = ~date, y = ~volume, 
                marker = list(color = vol_signal_colors[["SELL"]], 
                              size = 10, symbol = "x"),
                name = paste(sig, "SELL"),
                hoverinfo = "text",
                hovertemplate = paste("<b>Date:</b> %{x|%Y-%m-%d}<br><b>", 
                                      sig, "SELL</b><extra></extra>"))
}

ema_lines <- c("EMA5", "EMA8", "EMA13", "EMA20", "EMA50", "EMA200")

ema_colors <- c("EMA5" = "black", "EMA8" = "yellow",
                "EMA13" = "purple", "EMA20" = "red", 
                "EMA50" = "grey", "EMA200" = "blue")

for (ema in ema_lines) {
  volume_plot <- 
    volume_plot %>%
    add_lines(data = ema_signal_plot_html, 
          x = ~date, y = as.formula(paste0("~", ema)), name = ema, 
              line = list(color = ema_colors[ema]), yaxis = "y2",
              hoverinfo = "y+text", 
              hovertemplate = paste("<b>Date:</b> %{x|%Y-%m-%d}<br><b>", 
                                    ema, ":</b> %{y:.2f}<extra></extra>"))
}

volume_plot
```


`In Progress`


### **RSI**总结 Summary- **RSI**:  


`In Progress`


The program is now constructed to generate **daily trading signals** given by the **Relative Strength Index (RSI)** indicator values. The latest applied parameter settings and trading rules for the **RSI**-generated signals are summarized above. 

**Daily trading signals** from the **RSI** indicators, include `tsignal10`, `tsignal11` and `tsignal12`, for all stocks are generated; and the results (data tables and plots) for `AAPL.US` are shown above as illustrations, refer to the *webapp* for the complete data tables and plots/visualizations outputs.

根据**相对强弱指数（RSI）**指标值给出**每日交易信号**的模型程序现已构建完成。选股模型最新应用的指标参数设定和**RSI**策略生成的交易信号的相关分析和设定已在上述部分总结。

**RSI**指标的**每日交易信号**，包括`tsignal10`,`tsignal11`和`tsignal12`，且已经为模型中所有的股票生成**每日交易信号**；并且以`苹果公司(AAPL.US)`的结果（数据表和图表）作为示例展示，完整图表可参阅*webapp*。 

$^*$ Whether the **RSI** indicator, or the trading signals `tsignal10`, `tsignal11` and `tsignal12` are effective in selecting stocks to construct a portfolio trading strategies with upsides, will be further analyzed by the model, and refer to **$\S 4.1$ ** [选取有效的技术指标（动态更新）Dynamic: Selecting Effective Technical Indicators] below for more details. 

$^*$ **RSI**指标或策略交易信号`tsignal10`,`tsignal11`和`tsignal12`在组合交易策略中是否具备有效选择上升潜力股票的能力，将由选股模型进一步分析，详情参考**$\S 4.1$ ** [选取有效的技术指标（动态更新）Dynamic: Selecting Effective Technical Indicators]。

