## <span style="color:blue">技术指标5：布林带 Technical Indicator 5: Bollinger Bands (BBands)</span> 


```{r 305-98, message=FALSE, warning=FALSE, include=FALSE}
# Define function to read another rmd file
source_rmd <- function(file, local = FALSE, ...){
  options(knitr.duplicate.label = 'allow')

  tempR <- tempfile(tmpdir = ".", fileext = ".R")
  on.exit(unlink(tempR))
  knitr::purl(file, output=tempR, quiet = TRUE)

  envir <- globalenv()
  source(tempR, local = envir, ...)
}
```

```{r 305-99, message=FALSE, warning=FALSE, include=FALSE}
# Read in base model construction rmd to continue with 3.4
source_rmd("03_d_RSI.Rmd")
```


Includes `tsignal13`, `tsignal14`, `tsignal15a` and `tsignal15`

包括交易信号 `tsignal13`, `tsignal14`, `tsignal15a` 以及 `tsignal15`  

### **BBands**简介 Intro- **BBands**:  


`In Progress`


Mathematically defined as: 数学上定义为：

Bandwidth: determined by the asset volatility  

$$\text{Bandwidth}_{t}(n)=k \times stdev(P_{t},n)$$  

The lower and upper bands are:  

$$\text{up}_{t}=P_{t}+\text{Bandwidth}_{t}(n)$$  

$$\text{down}_{t}=P_{t}-\text{Bandwidth}_{t}(n)$$  

To denote the location of the price, we use  

$$\%B=\frac{P_{t}-\text{down}_{t}}{\text{up}_{t}-\text{down}_{t}}$$  

where it is greater 1 if it is above the upper band, and less than 0 when it is below the lower band.

`In Progress`

The program uses the formula above to compute the **Bollinger Bands (BBands)** values for **all stocks** in the model with various parameter settings, and creates appropriate related visualizations. The **BBands**-based **daily trading signals** will then be constructed from the subjectively set trading rules.  

`In Progress`

选股模型程序使用上述公式计算模型中**所有股票**的在多个不同的参数设定下的**布林带（BBands）**值，并创建相应的可视化图表。然后，根据主观设定的交易规则构建**BBands****日交易信号**。 

```{r 305-1, echo=FALSE, message=FALSE, warning=FALSE}
# Define a function to compute the value for SMA using the adjusted close price with parameter settings of n days 
# Same as 3.1
SMA_comput <- function(price, n){
  sma <- rep(NA, length(price)) 
  if (length(price) >= n) {  # Only compute SMA if enough data points are available
    for (i in n:length(price)){
      sma[i] <- mean(price[(i-n+1):i])
    }
  }
  return(sma)
}
```

```{r 305-2, echo=FALSE, message=FALSE, warning=FALSE}
# Define functions to compute the values for BBands (all components) using the adjusted close price with parameter settings of n days 

BBands_up_comput <- function(price, n, sd){
  mavg <- SMA_comput(price, n)
  sdev <- rep(NA, length(price))
  N <- length(price)
  if (N >= n) { # Only compute if enough data points are available
    for (i in (n+1):N){
      sdev[i] <- sd(price[(i-n+1):i])
    }
    sdev <- sqrt((n-1)/n) * sdev
    up <- mavg + sd * sdev
    return(up)
  } else {
    return(rep(NA, N))
  }
}


BBands_down_comput <- function(price, n, sd){
  mavg <- SMA_comput(price, n)
  sdev <- rep(NA, length(price))
  N <- length(price)
  if (N >= n) {
    for (i in (n+1):N){
      sdev[i] <- sd(price[(i-n+1):i])
    }
    sdev <- sqrt((n-1)/n) * sdev
    dn <- mavg - sd * sdev
    return(dn)
  } else {
    return(rep(NA, N))
  }
}


BBands_mavg_comput <- function(price, n){
  mavg <- SMA_comput(price, n)
  return(mavg)
}


BBands_pctB_comput <- function(price, n, sd){
  mavg <- SMA_comput(price, n)
  sdev <- rep(NA, length(price))
  N <- length(price)
  if (N >= n) {
    for (i in (n+1):N){
      sdev[i] <- sd(price[(i-n+1):i])
    }
    sdev <- sqrt((n-1)/n) * sdev
    up <- mavg + sd * sdev
    dn <- mavg - sd * sdev
    # Prevent division by zero
    range <- up - dn
    range[range == 0] <- NA  # replace 0s with NA to avoid division by zero
    pctB <- (price - dn) / range
    return(pctB)
  } else {
    return(rep(NA, N))
  }
}

```

```{r 305-3, message=FALSE, warning=FALSE, include=FALSE}
# Compute BBands for all stocks, Full Data
mega7data_modified <-
  mega7data_modified %>%
  group_by(symbol) %>%
  mutate(BBands_20_up = BBands_up_comput(adjusted, n = 20, sd = 2),
         BBands_20_down = BBands_down_comput(adjusted, n = 20, sd = 2),
         BBands_20_mavg = BBands_mavg_comput(adjusted, n = 20),
         BBands_20_pctB = BBands_pctB_comput(adjusted, n = 20, sd = 2))
```

```{r 305-4, message=FALSE, warning=FALSE, include=FALSE}
# Alternative way: 
# Below utilizes the `TTR` package directly for BBands computations: BBands()
# AAPL <- xts(bbands_value_result_pdf$adjusted,bbands_value_result_pdf$date)
# bbands <- BBands(AAPL,n = 20, sd = 2) 
```

```{r 305-5, message=FALSE, warning=FALSE, include=FALSE}
bbands_value_result <- 
  mega7data_modified %>%
  mutate(date = as.Date(date)) %>%
  select(date, adjusted,BBands_20_down, BBands_20_mavg, 
         BBands_20_up,BBands_20_pctB, volume) %>%
  arrange(desc(date)) %>%
  head(5000)

bbands_value_result_pdf <- 
  mega7data_modified %>%
  slice(which(symbol == "AAPL")) %>%
  mutate(date = as.Date(date)) %>%
  select(date, adjusted,BBands_20_down, BBands_20_mavg, 
         BBands_20_up,BBands_20_pctB, volume) %>%
  arrange(desc(date))
```

```{r 305-6, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}

# NOT FINISHED

# ##### [Code Hidden 代码已隐藏]{style="color:red"} {-}

# ##### [Individual stock outputs are suppressed, only `AAPL.US` related results are shown for illustration purposes. Refer to the *webapp* or the `html` version of the *e-Manual* for complete outputs. 个股输出数据及图表已隐藏，报告仅展示`苹果公司(AAPL.US)`的相关结果,完整图表可参阅*webapp* 或网页版*Global MAS 量化模型搭建说明*。]{style="color:red"} {-}

# pdf output
# Display AAPL output (EMA values)
kbl(head(ema_value_result_pdf,10), booktabs = T, linesep = '', digits = 1,
    caption = "EMA Computations for AAPL.US",
    format.args = list(big.mark = ",", scientific = FALSE),
    col.names = c("Symbol","Date","Adj Close","EMA5","EMA8",
                  "EMA13","EMA20","EMA50","EMA200","Volume")) %>%
  kable_styling(latex_options = c("striped", "scale_down",
                                  "HOLD_position"), 
                position = "center") %>%
  column_spec(c(1,4:9), bold = T) %>%
  kableExtra::footnote(general = "Output 3.2.a: Latest 10 rows of data are shown.")
```

##### [Code Hidden 代码已隐藏]{style="color:red"} {-}

##### [Enter the ticker/symbol in the search box for stock-specific results. Sort tool is available next to the variable names. 搜索框中输入股票代码可以过滤展示个股相关结果。点击变量名旁的箭头可进行排序。]{style="color:purple"} {-}

```{r 305-7, echo=FALSE, message=FALSE, warning=FALSE}
# html output
# Display BBands values
DT::datatable(bbands_value_result, 
              colnames = c('Symbol' = 2, 'Date' = 3, 'Adjusted' = 4, 
                           'BBands(20) Down' = 5,'BBands(20) Trend Line' = 6,
                           'BBands(20) Up' = 7,
                           'BBands(20) Price Location' = 8,
                           'Volume' = 9),
              caption = htmltools::tags$caption(style = 'caption-side: top; 
                                            text-align: center; color: black; 
                                            font-size: 200%;',
                                            'Bollinger Bands (BBands) Computations'),
              options = list(pageLength = 10, lengthMenu = c(5, 10, 15, 20),
              searching = TRUE, scrollX = TRUE,
              style = list(width = '100%')), extensions = 'Buttons') %>%
  formatRound(columns = c('Adjusted','BBands(20) Down','BBands(20) Trend Line',
                          'BBands(20) Up',
                          'BBands(20) Price Location'), digits = 2)  %>%
  formatRound(columns = 'Volume', digits = 0)
```

Output 3.5.a: **Bollinger Bands (BBands)** Computations, latest 10 rows of data are shown.  

图表 3.5.a: **Bollinger Bands (BBands)** 计算结果，展示最新的 10 行数据。

</br>

The program computed the **Bollinger Bands (BBands)** values for all stocks input in the model, with the parameter settings of $n = 20, k = 2$. As an illustration, above table shows the computed **Bollinger Bands (BBands)** values and plots (end of section). 

模型程序为输入的所有股票计算了**Bollinger Bands (BBands)**值，参数设定为$n = 20, k = 2$。作为示例，上表展示了计算的**Bollinger Bands (BBands)**值并创建了可视化图表（节末）。

```{r 305-8, message=FALSE, warning=FALSE, include=FALSE}
# Data manipulation for BBands plot AAPL.US
bbands_aapl_xts <- 
  mega7data_modified %>%
  slice(which(symbol == "AAPL")) %>%
  mutate(date = as.POSIXct(date)) %>%
  select(date, open, high, low, close, volume, adjusted) %>%
  na.omit()

open <- bbands_aapl_xts$open
high <- bbands_aapl_xts$high
low <- bbands_aapl_xts$low
close <- bbands_aapl_xts$close
adjusted <- bbands_aapl_xts$adjusted
volume <- as.numeric(bbands_aapl_xts$volume)

bbands_aapl_xts <- xts(cbind(open, high, low, close, volume, adjusted),
                   as.POSIXct(bbands_aapl_xts$date))
bbands_aapl_xts <- last(bbands_aapl_xts,'365 days')
```

```{r 305-9, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
##### AAPL Plot include BBands components using `TTR` package {-}
# pdf plot
# BBands plot AAPL.US n = 20, k = 2
chartSeries(bbands_aapl_xts,
            theme = chartTheme('black'))

addBBands(n = 20, sd = 2, maType = "SMA", on = 1)
```



### 交易信号与策略- **BBands** Trading signal(s) & strategies- **BBands**:

 

`In Progress`



### **BBands**策略交易信号汇总 To summarize for **BBands** trading signals:   

```{r eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
布林带 (Bollinger Bands，简称 BBANDS) 是由 John Bollinger 提出的一种流行的波动性指标，主要用来衡量价格的高低程度以及波动性。布林带由三条线组成：中线是移动平均线，上线和下线则是在中线的基础上加减标准差得到的。
布林带的计算公式如下：
1）计算收盘价序列的移动平均线（MID）。
2）计算收盘价序列的标准差（stdev）：
3）计算布林带的上线和下线：
4）计算布林带的宽度和价格在布林带中的位置：
以下是布林带一些主要的应用方法：
1）波动性度量：当布林带的宽度（上线与下线之间的距离）扩大时，表示市场波动性增大，可能预示着价格大幅波动的可能性增加；当布林带的宽度收窄时，表示市场波动性减小，可能预示着市场即将进入平静期。
2）超买超卖判断：布林带的上线和下线可被视为价格的相对高点和低点，通常，当价格触及上线时，市场可能处于超买状态，可能存在回落的可能性；反之，当价格触及下线时，市场可能处于超卖状态，可能存在反弹的可能性。
3）趋势判断：价格在布林带的中线上方运动，通常被认为是上升趋势；在中线下方运动，则可能表示下降趋势。
4）突破信号：当价格突破上线或者下线，特别是伴随着交易量的放大，可能预示着价格趋势的改变。但这种信号需要谨慎处理，因为有可能是假突破。
Buy signal arises when price is above the band.

Sell signal arises when price is below the band.
```


-   **BBands**- `tsignal13`:\
    **BUY**: $\text{BBands mavg} \leq \text{close price} < \text{BBands up}$,\
    **SELL**: $\text{BBands down} < \text{close price} \leq \text{BBands mavg}$,\
    **HOLD**: otherwise; 

- **BBands**交易信号- `tsignal13`:\
    **买入**: $\text{布林带中线} \leq \text{收盘价}  < \text{布林带上线}$,\
    **卖出**: $\text{布林带下线} < \text{收盘价}  \leq \text{布林带中线}$,\
    **持有**: 其他情况;

-   **BBands**- `tsignal14`:\ [overbuy oversold]
    **BUY**: $\text{close price}$ cross from **above to below** $\text{BBands down}$,\
    **SELL**: $\text{close price}$ cross from **below to above** $\text{BBands up}$, \
    **HOLD**: otherwise;  
    
- **BBands**交易信号- `tsignal14`:\ 
    **买入**: $\text{收盘价}$ **从上方穿越至** $\text{布林带下线}$**下方**,\
    **卖出**: $\text{收盘价}$ **从下方穿越至** $\text{布林带上线}$**上方**,\
    **持有**: 其他情况;
    
-   **BBands**- `tsignal15`:\
    **BUY**: $\text{close price} \leq \text{BBands down}$ **while** $\text{trading volume}$ **increased**,\
    **SELL**: $\text{close price} \geq \text{BBands up}$ **while** $\text{trading volume}$ **increased**, \
    **HOLD**: otherwise.  
    
- **BBands**交易信号- `tsignal15`:\
    **买入**: $\text{收盘价} \leq \text{布林带下线}$ **同时伴随** $\text{交易量}$ 上升, \
    **卖出**: $\text{收盘价} \geq \text{布林带上线}$ **同时伴随** $\text{交易量}$ 上升,\
    **持有**: 其他情况。

```{r 305-10, message=FALSE, warning=FALSE, include=FALSE}
# BBands Trading Signal 13: BBands mavg <= adjusted < BBands up
# BBands Trading Rule setup and Generate Signals 
mega7data_modified <- 
  mega7data_modified %>%
  group_by(symbol) %>%
  mutate(tsignal13 = case_when(
    BBands_20_mavg <= adjusted & adjusted < BBands_20_up ~ 'BUY',
    BBands_20_down < adjusted & adjusted < BBands_20_mavg ~ 'SELL',
    TRUE ~ 'HOLD'))
```

```{r 305-11, message=FALSE, warning=FALSE, include=FALSE}
# BBands Trading Signal 14: adjusted crossover below BBands down
# BBands Trading Rule setup and Generate Signals 
mega7data_modified <- 
  mega7data_modified %>%
  group_by(symbol) %>%
  mutate(tsignal14 = case_when(
    lag(adjusted) >= lag(BBands_20_down) & adjusted <= BBands_20_down ~ 'BUY',
    lag(adjusted) <= lag(BBands_20_up) & adjusted >= BBands_20_up ~ 'SELL',
    TRUE ~ 'HOLD'))
```

```{r 305-12, message=FALSE, warning=FALSE, include=FALSE}
# BBands Trading Signal 15a: adjusted <= BBands down 
# BBands Trading Signal 15: adjusted <= BBands down & trading volume increased
# BBands Trading Rule setup and Generate Signals 
mega7data_modified <- 
  mega7data_modified %>%
  group_by(symbol) %>%
  mutate(tsignal15a = case_when(
    adjusted <= BBands_20_down ~ 'BUY',
    adjusted >= BBands_20_up ~ 'SELL',
    TRUE ~ 'HOLD')) %>%
  mutate(tsignal15 = case_when(
    adjusted <= BBands_20_down & lag(volume) <= volume ~ 'BUY',
    adjusted >= BBands_20_up & lag(volume) <= volume ~ 'SELL',
    TRUE ~ 'HOLD'))
```

```{r 305-13, message=FALSE, warning=FALSE, include=FALSE, paged.print=TRUE}
# Prepare data frame BBands signal results
bbands_signal_result <-
  mega7data_modified %>%
  select(date, symbol, adjusted, tsignal13, 
         tsignal14, tsignal15a, tsignal15) %>%
  arrange(desc(date)) %>%
  head(5000)

# For AAPL signals results (BBands)
bbands_signal_result_pdf <-
  mega7data_modified %>%
  slice(which(symbol == "AAPL")) %>%
  ungroup() %>%
  select(date, symbol, adjusted, tsignal13, 
         tsignal14, tsignal15a, tsignal15) %>%
  arrange(desc(date)) %>%
  head(10)
```

```{r 305-14, eval=FALSE, fig.pos='H', message=FALSE, warning=FALSE, include=FALSE}

# NOT FINISHED

# ##### [Code Hidden 代码已隐藏]{style="color:red"} {-}

# ##### [Individual stock outputs are suppressed, only `AAPL.US` related results are shown for illustration purposes. Refer to the *webapp* or the `html` version of the *e-Manual* for complete outputs. 个股输出数据及图表已隐藏，报告仅展示`苹果公司(AAPL.US)`的相关结果,完整图表可参阅*webapp* 或网页版*Global MAS 量化模型搭建说明*。]{style="color:red"} {-}

# pdf output
# Display AAPL signal results (EMA signals)
kbl(ema_signal_result_pdf, booktabs = T, linesep = "", longtable = T, 
    digits = 1, caption = "EMA Trading Signals for AAPL.US", 
    format.args = list(big.mark = ",", scientific = FALSE),
    col.names = c("Date","Symbol","Adj Close","tsignal4","tsignal5",
                  "tsignal6","tsignal6a","tsignal6b")) %>%
  kable_styling(latex_options = c("striped", "scale_up",
                                  "HOLD_position"),
                full_width = F) %>%
  column_spec(c(2,4:6), bold = T) %>%
  column_spec(1, width = "1.9cm") %>%
  kableExtra::footnote(general = "Output 3.2.b: latest 10 rows of data are shown.",
              number = "Includes tsignal4, tsignal5, tsignal6, tsignal6a and tsignal6b.")
#图表3.2.b: EMA交易信号，展示最新的10行数据。包括`tsignal4`, `tsignal5`, `tsignal6`, #`tsignal6a`和`tsignal6b`。
```

##### [Code Hidden 代码已隐藏]{style="color:red"} {-}

##### [Enter the ticker/symbol in the search box for stock-specific results. Sort tool is available next to the variable names. 搜索框中输入股票代码可以过滤展示个股相关结果。点击变量名旁的箭头可进行排序。]{style="color:purple"} {-}

```{r 305-15, echo=FALSE, message=FALSE, warning=FALSE}
# html output
# Display BBands signal results 
DT::datatable(bbands_signal_result, 
              colnames = c('Date' = 2, 'Symbol' = 3, 'Adjusted' = 4,
                           'Signal 13' = 5, 'Signal 14' = 6, 
                           'Signal 15a' = 7, 'Signal 15' = 8),
              caption = htmltools::tags$caption(style = 'caption-side: top; 
                                            text-align: center; color: black; 
                                            font-size: 200%;',
                                            'Bollinger Bands (BBands) Trading Signals'),
              options = list(pageLength = 10, lengthMenu = c(5, 10, 15, 20),
              searching = TRUE, style = list(width = '100%')), 
              extensions = 'Buttons') %>%
    formatRound(columns = 'Adjusted', digits = 2)  
```

Output 3.5.b: **Bollinger Bands (BBands)** trading signals, latest 10 rows of data are shown. Includes `tsignal13`, `tsignal14`, `tsignal15a`, and `tsignal15`.  

图表3.5.b: **Bollinger Bands (BBands)**交易信号，展示最新的10行数据。包括`tsignal13`, `tsignal14`, `tsignal15a`, 和`tsignal15`。

```{r 305-16, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}

# NOT FINISHED

# pdf output
# EMA Candlestick+Volume Plot for AAPL with trading signals
# Prepare the dataset for candlestick components
ema_signal_plot_pdf<- 
  mega7data_modified %>%
  slice(which(symbol == "AAPL")) %>%
  select(date, symbol, adjusted, open, close, high, low, volume, EMA5, 
         EMA8, EMA13, EMA20, EMA50, EMA200, tsignal4, tsignal5, tsignal6) %>%
  mutate(date = as.Date(date, format = "%Y-%m-%d"),
         day_trend_color = ifelse(open - adjusted > 0, "red", "green")) %>%
  filter(as.Date(date) > as.Date(Sys.Date()-months(12)))
```

```{r 305-17, eval=FALSE, fig.height=7, fig.width=10, message=FALSE, warning=FALSE, include=FALSE}

# NOT FINISHED

# pdf output
# EMA Candlestick+Volume Plot for AAPL with trading signals

# Candlestick Plot with EMA Trading Signals
color_values <- c(
  "EMA5" = "black", 
  "EMA8" = "yellow", 
  "EMA13" = "purple", 
  "EMA20" = "red", 
  "EMA50" = "grey", 
  "EMA200" = "blue",
  "green" = "darkgreen", 
  "red" = "red",
  "Signal4 BUY " = "lightgreen", 
  "Signal4 SELL" = "deeppink",
  "Signal5 BUY" = "lightgreen", 
  "Signal5 SELL" = "deeppink",
  "Signal6 BUY" = "lightgreen", 
  "Signal6 SELL" = "deeppink"
)

candlestick <- 
  ggplot(ema_signal_plot_pdf, aes(x = date)) +
  geom_segment(aes(xend = date, y = open, 
                   yend = adjusted, colour = day_trend_color), size = 5) +
  geom_segment(aes(xend = date, y = high, 
                   yend = low, colour = day_trend_color)) +
  geom_line(aes(y = EMA5, color = "EMA5"), size = 0.5) +
  geom_line(aes(y = EMA8, color = "EMA8"), size = 0.5) +
  geom_line(aes(y = EMA13, color = "EMA13"), size = 0.5) +
  geom_line(aes(y = EMA20, color = "EMA20"), size = 0.5) +
  geom_line(aes(y = EMA50, color = "EMA50"), size = 0.5) +
  geom_line(aes(y = EMA200, color = "EMA200"), size = 0.5) +

  # Adding trading signals with different shapes and colors
  geom_point(data = filter(ema_signal_plot_pdf, tsignal4 == "BUY"),
             aes(x = date, y = high, color = "Signal4 BUY", 
                 shape = "Signal4 BUY"), size = 2) +
  geom_point(data = filter(ema_signal_plot_pdf, tsignal4 == "SELL"), 
             aes(x = date, y = low, color = "Signal4 SELL", 
                 shape = "Signal4 SELL"), size = 2) +
  geom_point(data = filter(ema_signal_plot_pdf, tsignal5 == "BUY"), 
             aes(x = date, y = high, color = "Signal5 BUY", 
                 shape = "Signal5 BUY"), size = 2) +
  geom_point(data = filter(ema_signal_plot_pdf, tsignal5 == "SELL"), 
             aes(x = date, y = low, color = "Signal5 SELL", 
                 shape = "Signal5 SELL"), size = 2) +
  geom_point(data = filter(ema_signal_plot_pdf, tsignal6 == "BUY"), 
             aes(x = date, y = high, color = "Signal6 BUY", 
                 shape = "Signal6 BUY"), size = 2) +
  geom_point(data = filter(ema_signal_plot_pdf, tsignal6 == "SELL"), 
             aes(x = date, y = low, color = "Signal6 SELL", 
                 shape = "Signal6 SELL"), size = 2) +
  theme(legend.position = "top",
            guides(color = guide_legend(nrow = 4, byrow = TRUE, 
                                title = "Indicators & Signals"), 
    shape = guide_legend(nrow = 4, byrow = TRUE, title = "Trade Signals") 
  )) +
  scale_color_manual(name = "Indicators & Signals", values = color_values) +
  scale_shape_manual(name = "Signal Shapes", 
                     values = c("Signal4 BUY" = 17, "Signal4 SELL" = 4, 
                                "Signal5 BUY" = 18, "Signal5 SELL" = 3, 
                                "Signal6 BUY" = 15, "Signal6 SELL" = 1)) +
  labs(
    y = "Stock Price, in USD", x = "Date") +
    labs(title = paste0("Price Volume Candlestick Plot for TLSA.US \
       with EMA Lines and Trading Signals")) +
  theme_bw() +
  scale_x_date(date_breaks = "2 months", date_labels = "%b %Y")

# Volume Plot
volume_plot <- 
  ggplot(ema_signal_plot_pdf, aes(x = date, y = volume, fill = day_trend_color)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = c("green" = "darkgreen", "red" = "red")) +
  labs(y = "Daily Trading Volume", x = "Date") +
  theme_bw() +
  theme(legend.position = "none",
            guides(color = guide_legend(nrow = 4, byrow = TRUE, 
                                title = "Indicators & Signals"), 
    shape = guide_legend(nrow = 4, byrow = TRUE, title = "Trade Signals") 
  )) +
  scale_x_date(date_breaks = "2 months", date_labels = "%b %Y") +
  scale_y_continuous(labels = scales::comma)


# Combine 2 plots
ggarrange(candlestick, volume_plot, ncol = 1, nrow = 2,
    heights =c(9,3), widths = 10, align = "v") 

# Output 3.1.c: EMA plot with trading signals on Price and Volume, duration setting TTM.
```

```{r 305-18, echo=FALSE, message=FALSE, warning=FALSE}
# html output
# plotly interactive plot
# BBands Candlestick+Volume Plot for AAPL with trading signals
# Prepare the dataset 

bbands_signal_plot_html<- 
  mega7data_modified %>%
  slice(which(symbol == "AAPL")) %>%
  select(date, symbol, adjusted, open, close, high, low, volume, BBands_20_down, 
         BBands_20_mavg, BBands_20_up, BBands_20_pctB, tsignal13, tsignal14,
         tsignal15a, tsignal15) %>%
  mutate(date = as.Date(date, format = "%Y-%m-%d"),
         day_trend_color =  ifelse(open < adjusted, "lightgreen", "red"),
         prev_volume = lag(volume),
         prev_adjusted = lag(adjusted),
         prev_BBands_20_down = lag(BBands_20_down),
         prev_BBands_20_mavg = lag(BBands_20_mavg),
         prev_BBands_20_up = lag(BBands_20_up),
         prev_BBands_20_pctB = lag(BBands_20_pctB),
         volume_color = ifelse(volume > prev_volume, "orange", "lightblue"),
         hover_text_volume = paste(
      "<b>Symbol:</b>", symbol, "<br>",
      "<b>Date:</b>", format(date, '%Y-%m-%d'), "<br>",
      "<b>Daily Volume:</b>", formatC(volume, big.mark = ","),
      "<span style='color:", 
      ifelse(volume > prev_volume, "darkgreen", "red"), ";'>",
      ifelse(volume > prev_volume, "▲", "▼"), "</span>", "<br>")) %>% 
 filter(as.Date(date) > as.Date(Sys.Date()-months(12)))

# Define shapes for each signal
signal_shapes <- list(
  "Signal13 BUY" = "circle",
  "Signal13 SELL" = "circle-open",
  "Signal14 BUY" = "triangle-up",
  "Signal14 SELL" = "triangle-down-open",
  "Signal15a BUY" = "square",
  "Signal15a SELL" = "square-open",
  "Signal15 BUY" = "diamond",
  "Signal15 SELL" = "diamond-open"
)

bbands_signal_plot_html <- 
  bbands_signal_plot_html %>%
  mutate(hover_text = paste(
    "<b>Symbol:</b>", symbol, "<br>",
    "<b>Date:</b>", format(date, '%Y-%m-%d'), "<br>",
    "<b>Adjusted Close Price:</b> $", round(adjusted, 2), "<br>",
    "<span style='color:", 
    ifelse(adjusted > prev_adjusted, "darkgreen", "pink"), ";'>",
      ifelse(adjusted > prev_adjusted, "▲", "▼"), "</span>", "<br>",
    "<b>Open:</b> $", round(open, 2), "<br>",
    "<b>High:</b> $", round(high, 2), "<br>",
    "<b>Low:</b> $", round(low, 2), "<br>",
    "<b>Volume:</b>", formatC(volume, format = "f", big.mark = ","),
     "<span style='color:", 
      ifelse(volume > prev_volume, "darkgreen", "red"), ";'>",
      ifelse(volume > prev_volume, "▲", "▼"), "</span>", "<br>"
  )) 

# Hover for BBands subplot
bbands_signal_plot_html <- 
  bbands_signal_plot_html %>%
  mutate(hover_text_bbands = paste(
      "<b>Symbol:</b>", symbol, "<br>", 
      "<b>Date:</b>", format(date, '%Y-%m-%d'), "<br>",
      "<b>Adjusted Close Price:</b> $", round(adjusted, 2), 
      "<span style='color:", 
      ifelse(adjusted > prev_adjusted, "darkgreen", "red"), ";'>",
      ifelse(adjusted > prev_adjusted, "▲", "▼"), "</span>", "<br>",
      "<b>BBands Down:</b>", round(BBands_20_down, 2),
      "<span style='color:", 
      ifelse(BBands_20_down > prev_BBands_20_down, "darkgreen", "deeppink"), ";'>",
      ifelse(BBands_20_down > prev_BBands_20_down, "▲", "▼"), "</span>", "<br>",
      "<b>BBands Trend:</b>", round(BBands_20_mavg, 2),
      "<span style='color:", 
      ifelse(BBands_20_mavg > prev_BBands_20_mavg, "darkgreen", "deeppink"), ";'>",
      ifelse(BBands_20_mavg > prev_BBands_20_mavg, "▲", "▼"), "</span>", "<br>",
      "<b>BBands Up</b>", round(BBands_20_up, 2),
      "<span style='color:", 
      ifelse(BBands_20_up > prev_BBands_20_up, "darkgreen", "deeppink"), ";'>",
      ifelse(BBands_20_up > prev_BBands_20_up, "▲", "▼"), "</span>", "<br>",
      "<b>BBands Price Location</b>", round(BBands_20_pctB, 2),
      "<span style='color:", 
      ifelse(BBands_20_pctB > prev_BBands_20_pctB, "darkgreen", "deeppink"), ";'>",
      ifelse(BBands_20_pctB > prev_BBands_20_pctB, "▲", "▼"), "</span>", "<br>"
    )
  )
```

##### [Code Hidden 代码已隐藏]{style="color:red"} {-}

##### [Individual stock outputs are suppressed, only `AAPL.US` related results are shown for illustration purposes. Refer to the *webapp* for the complete plot output. 个股输出数据及图表已隐藏，报告仅展示`苹果公司(AAPL.US)`的相关结果,完整图表可参阅*webapp*。]{style="color:red"} {-}

```{r 305-19, echo=FALSE, fig.height=7, fig.width=12, message=FALSE, warning=FALSE}
# html output
# plotly interactive plot
# BBands Price Candlestick Plot for AAPL with trading signals

# Candlestick Plot with BBands Trading Signals
fig <- plot_ly(data = bbands_signal_plot_html, type = "candlestick", 
               x = ~date, open = ~open, close = ~adjusted, high = ~high, low = ~low,
               increasing = list(line = list(color = "darkgreen", width = 10), 
                                 fillcolor = "darkgreen"),
               decreasing = list(line = list(color = "red", width = 10), 
                                 fillcolor = "red"), 
               hoverinfo = "text", text = ~hover_text, showlegend = FALSE) %>%
  add_lines(y = ~BBands_20_up, name = "BBands Up", 
            line = list(color = "red", dash = "dash", width = 3), showlegend = TRUE,
            hoverinfo = "y+text", 
            text = ~hover_text_bbands) %>%
  add_lines(y = ~BBands_20_mavg, name = "BBands Trend Line", 
            line = list(color = "darkgrey", width = 3),  showlegend = TRUE,
            hoverinfo = "y+text", 
            text = ~hover_text_bbands ) %>%
  add_lines(y = ~BBands_20_down, name = "BBands Down", 
            line = list(color = "red", dash = "dash", width = 3), showlegend = TRUE,
            hoverinfo = "y+text", 
            text = ~hover_text_bbands) %>% 
  add_markers(data = filter(bbands_signal_plot_html, tsignal13 == "BUY"), 
              x = ~date, y = ~high, 
              marker = list(color = "lightgreen", size = 6,
                            symbol = signal_shapes[["Signal13 BUY"]]), 
              name = "Signal13 BUY", showlegend = TRUE,
              hoverinfo = "text",
              hovertemplate = 
                "<b>Date:</b> %{x|%Y-%m-%d}<br><b>Signal13 BUY</b><extra></extra>") %>%
  add_markers(data = filter(bbands_signal_plot_html, tsignal13 == "SELL"), 
              x = ~date, y = ~low, 
              marker = list(color = "pink", size = 6,
                            symbol = signal_shapes[["Signal13 SELL"]]), 
              name = "Signal13 SELL", showlegend = TRUE,
              hoverinfo = "text",
              hovertemplate = 
                "<b>Date:</b> %{x|%Y-%m-%d}<br><b>Signal13 SELL</b><extra></extra>") %>%
  add_markers(data = filter(bbands_signal_plot_html, tsignal14 == "BUY"), 
              x = ~date, y = ~high, 
              marker = list(color = "lightgreen", size = 6,
                            symbol = signal_shapes[["Signal14 BUY"]]), 
              name = "Signal14 BUY",  showlegend = TRUE,
              hoverinfo = "text",
              hovertemplate = 
                "<b>Date:</b> %{x|%Y-%m-%d}<br><b>Signal14 BUY</b><extra></extra>") %>%
  add_markers(data = filter(bbands_signal_plot_html, tsignal14 == "SELL"), 
              x = ~date, y = ~low, 
              marker = list(color = "pink", size = 6,
                            symbol = signal_shapes[["Signal14 SELL"]]), 
              name = "Signal14 SELL", showlegend = TRUE,
              hoverinfo = "text",
              hovertemplate = 
                "<b>Date:</b> %{x|%Y-%m-%d}<br><b>Signal14 SELL</b><extra></extra>") %>%
  add_markers(data = filter(bbands_signal_plot_html, tsignal15a == "BUY"), 
              x = ~date, y = ~high, 
              marker = list(color = "lightgreen", size = 6,
                            symbol = signal_shapes[["Signal15a BUY"]]), 
              name = "Signal15a BUY", showlegend = TRUE,
              hoverinfo = "text",
              hovertemplate = 
                "<b>Date:</b> %{x|%Y-%m-%d}<br><b>Signal15a BUY</b><extra></extra>") %>%
  add_markers(data = filter(bbands_signal_plot_html, tsignal15a == "SELL"), 
              x = ~date, y = ~low, 
              marker = list(color = "pink", size = 6,
                            symbol = signal_shapes[["Signal15a SELL"]]), 
              name = "Signal15a SELL", showlegend = TRUE,
              hoverinfo = "text",
              hovertemplate = 
              "<b>Date:</b> %{x|%Y-%m-%d}<br><b>Signal15a SELL</b><extra></extra>") %>%
  add_markers(data = filter(bbands_signal_plot_html, tsignal15 == "BUY"), 
              x = ~date, y = ~high, 
              marker = list(color = "lightgreen", size = 6,
                            symbol = signal_shapes[["Signal15 BUY"]]), 
              name = "Signal15 BUY", showlegend = TRUE,
              hoverinfo = "text",
              hovertemplate = 
                "<b>Date:</b> %{x|%Y-%m-%d}<br><b>Signal15 BUY</b><extra></extra>") %>%
  add_markers(data = filter(bbands_signal_plot_html, tsignal15 == "SELL"), 
              x = ~date, y = ~low, 
              marker = list(color = "pink", size = 6,
                            symbol = signal_shapes[["Signal15 SELL"]]), 
              name = "Signal15 SELL", showlegend = TRUE,
              hoverinfo = "text",
              hovertemplate = 
              "<b>Date:</b> %{x|%Y-%m-%d}<br><b>Signal15 SELL</b><extra></extra>") %>%
  
  layout(title = list(text = "Interactive Price Candlestick Plot for AAPL.US \
                      with Bollinger Bands (BBands)  and Trading Signals",
                      x = 0.5,  
                      y = 1.2,  
                      xanchor = 'center',
                      yanchor = 'top'),
         xaxis = list(title = "Date", 
                      type = "date", 
                      rangeslider = list(visible = TRUE),
                      rangeselector = list(
                        buttons = list(
                          list(count = 1, label = "1w", 
                               step = "week", stepmode = "backward"),
                          list(count = 2, label = "2w", 
                               step = "week", stepmode = "backward"),
                          list(count = 1, label = "1m", 
                               step = "month", stepmode = "backward"),
                          list(count = 6, label = "6m", 
                               step = "month", stepmode = "backward"),
                          list(count = 12, label = "TTM", 
                               step = "month", stepmode = "backward"),
                          list(count = 1, label = "YTD",
                               step = "year", stepmode = "todate"),
                          list(count = 1, label = "1y", 
                               step = "year", stepmode = "backward"),
                          list(step = "all")
                      )
                    )),
         yaxis = list(title = "Stock Price, in USD", fixedrange = FALSE),
         legend = list(orientation = "h",x = 0, y = -0.6, 
                       xanchor = "left", yanchor = "top", traceorder = "normal"),
         margin = list(t = 100, b = 200),
         width = 800, height = 650)

fig
```
</br>

Output 3.5.c: Interactive **Bollinger Bands (BBands)** plot with trading signals on Price, duration setting TTM.  

图表 3.5.c: 交互式**布林带（BBands）**股价图表，包括**Bollinger Bands (BBands)**策略交易信号，时间设置为TTM。

##### [Code Hidden 代码已隐藏]{style="color:red"} {-}

##### [Individual stock outputs are suppressed, only `AAPL.US` related results are shown for illustration purposes. Refer to the *webapp* for the complete plot output. 个股输出数据及图表已隐藏，报告仅展示`苹果公司(AAPL.US)`的相关结果,完整图表可参阅*webapp*。]{style="color:red"} {-}

```{r 305-20, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}

# NOT FINISHED

# html output
# plotly interactive plot
# EMA Volume Plot for AAPL with trading signals
# Define signal colors and shapes for trading signals

volume_plot <- plot_ly(data = ema_signal_plot_html, 
                       x = ~date, y = ~volume, type = 'bar', 
                       marker = list(color = ~volume_color),
                       hoverinfo = 'text', text = ~hover_text_volume,
                       name = "Trading Volume") %>%
  layout(title = list(text = "Interactive Daily Trading Volume Plot for TLSA.US \
                      with EMA Lines and Trading Signals", 
                      x = 0.5, y = 0.95, 
                      xanchor = 'center', yanchor = 'top'),
         xaxis = list(title = "Date", type = "date", rangeslider = list(visible = TRUE),
                      rangeselector = list(
                        buttons = list(
                          list(count = 1, label = "1w", 
                               step = "week", stepmode = "backward"),
                          list(count = 2, label = "2w", 
                               step = "week", stepmode = "backward"),
                          list(count = 1, label = "1m", 
                               step = "month", stepmode = "backward"),
                          list(count = 6, label = "6m", 
                               step = "month", stepmode = "backward"),
                          list(count = 12, label = "TTM", 
                               step = "month", stepmode = "backward"),
                          list(count = 1, label = "YTD",
                               step = "year", stepmode = "todate"),
                          list(count = 1, label = "1y", 
                               step = "year", stepmode = "backward"),
                          list(step = "all")
                      )
                    )),
         yaxis = list(title = "Daily Trading Volume", fixedrange = FALSE, side = "left"),
         yaxis2 = list(title = "Daily EMA Values", 
                       overlaying = "y", side = "right", 
                       showgrid = FALSE,titlefont = list(size = 14)),
         barmode = 'group',
         legend = list(orientation = "h", x = 0.5, y = -0.4, 
                       xanchor = "center", yanchor = "top"),
         margin = list(l = 40, r = 40,b = 100, t = 100, pad = 4), height = 450)

vol_signal_colors <- c("BUY" = "lightgreen", "SELL" = "pink")
signals <- c("tsignal4", "tsignal5", "tsignal6")

for (sig in signals) {
  volume_plot <- volume_plot %>%
    add_markers(data = ema_signal_plot_html %>% 
                  filter(get(sig) == "BUY"), 
                x = ~date, y = ~volume, 
                marker = list(color = vol_signal_colors[["BUY"]], 
                              size = 10, symbol = "circle"),
                name = paste(sig, "BUY"),
                hoverinfo = "text",
                hovertemplate = paste("<b>Date:</b> %{x|%Y-%m-%d}<br><b>", 
                                      sig, "BUY</b><extra></extra>")) %>%
    add_markers(data = ema_signal_plot_html %>% filter(get(sig) == "SELL"), 
                x = ~date, y = ~volume, 
                marker = list(color = vol_signal_colors[["SELL"]], 
                              size = 10, symbol = "x"),
                name = paste(sig, "SELL"),
                hoverinfo = "text",
                hovertemplate = paste("<b>Date:</b> %{x|%Y-%m-%d}<br><b>", 
                                      sig, "SELL</b><extra></extra>"))
}

ema_lines <- c("EMA5", "EMA8", "EMA13", "EMA20", "EMA50", "EMA200")

ema_colors <- c("EMA5" = "black", "EMA8" = "yellow",
                "EMA13" = "purple", "EMA20" = "red", 
                "EMA50" = "grey", "EMA200" = "blue")

for (ema in ema_lines) {
  volume_plot <- 
    volume_plot %>%
    add_lines(data = ema_signal_plot_html, 
          x = ~date, y = as.formula(paste0("~", ema)), name = ema, 
              line = list(color = ema_colors[ema]), yaxis = "y2",
              hoverinfo = "y+text", 
              hovertemplate = paste("<b>Date:</b> %{x|%Y-%m-%d}<br><b>", 
                                    ema, ":</b> %{y:.2f}<extra></extra>"))
}

volume_plot
```

`In Progress`

### **BBands**总结 Summary- **BBands**:  

`In Progress`


The program is now constructed to generate **daily trading signals** given by the **Bollinger Bands (BBands)** indicator values. The latest applied parameter settings and trading rules for the **BBands**-generated signals are summarized above. 

**Daily trading signals** from the **BBands** indicators, include `tsignal13`, `tsignal14`, `tsignal15a` and `tsignal15`, for all stocks are generated; and the results (data tables and plots) for `AAPL.US` are shown above as illustrations, refer to the *webapp* for the complete data tables and plots/visualizations outputs.

根据**布林带（BBands）**指标值给出**每日交易信号**的模型程序现已构建完成。选股模型最新应用的指标参数设定和**BBands**策略生成的交易信号的相关分析和设定已在上述部分总结。

**BBands**指标的**每日交易信号**，包括`tsignal13`,`tsignal14`, `tsignal15a` 和`tsignal15`，且已经为模型中所有的股票生成**每日交易信号**；并且以`苹果公司(AAPL.US)`的结果（数据表和图表）作为示例展示，完整图表可参阅*webapp*。 

$^*$ Whether the **BBands** indicator, or the trading signals `tsignal13`, `tsignal14`, `tsignal15a` and `tsignal15` are effective in selecting stocks to construct a portfolio trading strategies with upsides, will be further analyzed by the model, and refer to **$\S 4.1$ ** [选取有效的技术指标（动态更新）Dynamic: Selecting Effective Technical Indicators] below for more details. 

$^*$ **BBands**指标或策略交易信号`tsignal13`,`tsignal14`, `tsignal15a` 和`tsignal15`在组合交易策略中是否具备有效选择上升潜力股票的能力，将由选股模型进一步分析，详情参考**$\S 4.1$ ** [选取有效的技术指标（动态更新）Dynamic: Selecting Effective Technical Indicators]。




