## <span style="color:blue">技术指标6：变化率 Technical Indicator 6: Rate of Change (ROC)</span> 


```{r 306-98, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
# Define function to read another rmd file
source_rmd <- function(file, local = FALSE, ...){
  options(knitr.duplicate.label = 'allow')

  tempR <- tempfile(tmpdir = ".", fileext = ".R")
  on.exit(unlink(tempR))
  knitr::purl(file, output=tempR, quiet = TRUE)

  envir <- globalenv()
  source(tempR, local = envir, ...)
}
```

```{r 306-99, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
# Read in base model construction rmd to continue with 3.4
#source_rmd("03_e_BB.Rmd")
```

`In Progress`

To put this in practice, if an increase in volume is observed with a steady increase in price, the instrument can be viewed as steady and strong.
However, if volume and price are changing in different directions, a reversal might be happened.

-   In terms of trading price, traders often observed the trends based on the charts shape and cross in ways that form shapes - often times with weird names like ‘head and shoulder’, ’ reverse head and sholder’, ‘double top’, ‘golden cross’, etc. A golden cross indicates a long term bull market going forward, whereas the death cross is the exact opposite, indicating a potential long term bear market. Both of these refer to the confirmation of long term trend by the occurance of the overlapping of moving average lines as shown below.












